---
title: "H1, H4, H5 -- Direct Replication of Abou-Chadi & Krause (2020, BJPS)"
output: html_document
---

Mirrors Abou-Chadi & Krause's published method on our own data as closely as
possible, for all three hypotheses. Outcome = `miljø_afhængig` (mainstream
party's environmental position, a MARPOR log-ratio built the same way as
their radical-right contagion variable), running variable =
`centered_lagged_pervote_samlet` (Green party's lagged vote share minus the
country's electoral threshold), treatment = `lagged_i_parlament` (Green
party in parliament; sharp cutoff at 0).

Nothing added beyond their specification: IK bandwidth, triangular kernel
weighting, country fixed effects, two-way clustered SEs by party and
election date (their actual clust1/clust2, confirmed from their published
source code `rrp_rdd.R` / `rrp_rdd_functions.R`). Reports their full Table
2-style structure -- 4 rows per hypothesis, not just one: non-parametric
p=1/p=2 (IK bandwidth, kernel-weighted) and parametric p=3/p=4 (global
sample, unweighted). No robustness battery beyond that, no bandwidth
sensitivity check, no bias-corrected CI -- this reports exactly what their
paper reports and nothing more, run end to end.

## Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
pacman::p_load(dplyr, fixest)

# rdd was archived on CRAN in 2025, so pacman::p_load()'s normal
# install.packages("rdd") fails silently and leaves IKbandwidth()
# undefined. Install the last CRAN release straight from the archive
# instead, if it isn't already installed.
if (!requireNamespace("rdd", quietly = TRUE)) {
  if (!requireNamespace("remotes", quietly = TRUE)) install.packages("remotes")
  remotes::install_version("rdd", version = "0.57", repos = "http://cran.r-project.org")
}
library(rdd)
```

```{r load-data}
final_dataset <- readRDS("final_dataset_publisering.rds")
```

## Shared estimator

Exactly Abou-Chadi & Krause's specification, reproducing all 4 rows of their
Table 2 structure for a given subgroup:

- **p = 1, p = 2** (their "Non-Parametric" rows): IK bandwidth
  (`rdd::IKbandwidth`), triangular kernel weights (`rdd::kernelwts`), local
  polynomial of that order around the cutoff.
- **p = 3, p = 4** (their "Parametric" rows): same polynomial regression,
  but unweighted and run on the full subgroup sample (no bandwidth
  restriction) -- their global specification.

All 4 rows use country fixed effects and two-way clustered SEs by party and
edate (their clust1/clust2). Fixed effect is country only, matching their
actual specification -- edate is their clust2 (a clustering variable), not
a second fixed effect: adding edate as an FE alongside country made
treatment and the running variable collinear with the FE within the narrow
IK-bandwidth window (constant within each country-election), so the model
couldn't be estimated.

```{r ack-row-function}
# One row of their Table 2: polynomial order p, with or without the IK
# bandwidth restriction and kernel weighting (bandwidth = NULL means their
# parametric/global row).
ack_row <- function(data, p, bandwidth, approach_label) {
  if (!is.null(bandwidth)) {
    data$kernel_weight <- kernelwts(
      X = data$centered_lagged_pervote_samlet,
      center = 0,
      bw = bandwidth,
      kernel = "triangular"
    )
    data <- data[data$kernel_weight > 0, ]
  } else {
    data$kernel_weight <- 1
  }

  # Explicit polynomial + treatment-interaction terms (equivalent to their
  # poly(force.var, p) + poly(force_above, p)) rather than formula-level
  # poly()/":" syntax.
  poly_terms  <- character(0)
  inter_terms <- character(0)
  for (j in 1:p) {
    xcol <- paste0(".x", j)
    tcol <- paste0(".Tx", j)
    data[[xcol]] <- data$centered_lagged_pervote_samlet^j
    data[[tcol]] <- data$lagged_i_parlament * data$centered_lagged_pervote_samlet^j
    poly_terms  <- c(poly_terms, xcol)
    inter_terms <- c(inter_terms, tcol)
  }

  fml <- as.formula(paste0(
    "miljø_afhængig ~ lagged_i_parlament + ", paste(poly_terms, collapse = " + "),
    " + ", paste(inter_terms, collapse = " + "), " | country"
  ))

  # Sharp design: lagged_i_parlament is a deterministic function of the
  # running variable's sign, so their ivreg() (sharp treatment as its own
  # instrument) is numerically identical to weighted OLS -- feols()
  # reproduces the same point estimate and SE given the same weights and
  # clustering.
  model <- feols(fml, data = data, weights = ~kernel_weight, cluster = ~party + edate)

  data.frame(
    Approach   = approach_label,
    Polynomial = p,
    Bandwidth  = if (is.null(bandwidth)) NA_real_ else round(bandwidth, 3),
    LATE       = round(coef(model)["lagged_i_parlament"], 3),
    StdError   = round(fixest::se(model)["lagged_i_parlament"], 3),
    pvalue     = round(fixest::pvalue(model)["lagged_i_parlament"], 4),
    N_below_c  = sum(data$centered_lagged_pervote_samlet < 0),
    N_above_c  = sum(data$centered_lagged_pervote_samlet >= 0)
  )
}

# Their full 4-row Table 2 structure for one subgroup: IK bandwidth is
# computed once per subgroup and shared by the two Non-Parametric rows,
# exactly as in their paper.
ack_replicate <- function(data, label) {
  bw <- IKbandwidth(
    X = data$centered_lagged_pervote_samlet,
    Y = data$miljø_afhængig,
    cutpoint = 0
  )

  tbl <- rbind(
    ack_row(data, p = 1, bandwidth = bw,   approach_label = "Non-Parametric"),
    ack_row(data, p = 2, bandwidth = bw,   approach_label = "Non-Parametric"),
    ack_row(data, p = 3, bandwidth = NULL, approach_label = "Parametric"),
    ack_row(data, p = 4, bandwidth = NULL, approach_label = "Parametric")
  )
  tbl$Group <- label

  cat("\n====", label, "====\n")
  print(tbl)

  tbl
}
```

## H1 -- Pooled effect across all mainstream parties

```{r h1}
h1_data <- final_dataset[complete.cases(final_dataset[, c(
  "miljø_afhængig", "centered_lagged_pervote_samlet", "lagged_i_parlament",
  "country", "edate", "party"
)]), ]

h1_result <- ack_replicate(h1_data, "H1 (Pooled)")
```

## H4 -- Moderation by mainstream party ideology (left vs. right)

```{r h4}
h4_data <- final_dataset[complete.cases(final_dataset[, c(
  "miljø_afhængig", "centered_lagged_pervote_samlet", "lagged_i_parlament",
  "left_party_lag1", "country", "edate", "party"
)]), ]

h4_right <- subset(h4_data, left_party_lag1 == 0)
h4_left  <- subset(h4_data, left_party_lag1 == 1)

h4_right_result <- ack_replicate(h4_right, "H4 (Right-Wing)")
h4_left_result  <- ack_replicate(h4_left,  "H4 (Left-Wing)")
```

## H5 -- Moderation by mainstream party size (large vs. small)

```{r h5}
h5_data <- final_dataset[complete.cases(final_dataset[, c(
  "miljø_afhængig", "centered_lagged_pervote_samlet", "lagged_i_parlament",
  "large_party_lag1", "country", "edate", "party"
)]), ]

h5_large <- subset(h5_data, large_party_lag1 == 1)
h5_small <- subset(h5_data, large_party_lag1 == 0)

h5_large_result <- ack_replicate(h5_large, "H5 (Large Parties)")
h5_small_result <- ack_replicate(h5_small, "H5 (Small Parties)")
```

## Combined summary table

```{r combined-table}
ack_results <- rbind(
  h1_result,
  h4_right_result, h4_left_result,
  h5_large_result, h5_small_result
)
ack_results <- ack_results[, c("Group", "Approach", "Polynomial", "Bandwidth",
                                "LATE", "StdError", "pvalue", "N_below_c", "N_above_c")]

knitr::kable(ack_results, caption = "Abou-Chadi & Krause-style replication: all results (Table 2 structure, 4 rows per hypothesis)")

dir.create("Publisering Analyse/AC&K Replication", showWarnings = FALSE)
write.csv(ack_results, "Publisering Analyse/AC&K Replication/ack_replication_results.csv", row.names = FALSE)
```
