---
title: "Green Parties Analysis - Refactored"
author: "Tobias"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Load Required Packages

```{r load_packages}
# Install pacman if not already installed
if (!require("pacman")) install.packages("pacman")

# Use pacman to load all required packages
pacman::p_load(
  # Data manipulation
  dplyr, tidyr, magrittr, purrr, data.table, readr, lubridate,
  
  # Visualization
  ggplot2,
  
  # Statistical analysis
  rdd, rddtools, rddensity, rdrobust, rdlocrand, AER, lmtest, sandwich,
  stargazer, broom, memisc, strucchange, plm,
  
  # Specific data sources
  manifestoR
)
```

## Helper Functions

```{r helper_functions}
# Function to filter European countries
filter_european_countries <- function(data, country_col = "country_name") {
  european_countries <- c(
    "Austria", "Bulgaria", "Croatia", "Czech Republic", "Denmark", 
    "Estonia", "Finland", "Germany", "Greece", "Ireland", "Italy", 
    "Latvia", "Luxembourg", "Netherlands", "Norway", "Poland", 
    "Portugal", "Romania", "Slovakia", "Slovenia", "Spain", 
    "Sweden", "Switzerland"
  )
  
  filter(data, !!sym(country_col) %in% european_countries)
}

# Function to calculate Lowe's RILE score
calculate_rile_lowe <- function(data) {
  right_cols <- c("per104", "per201", "per203", "per305", "per401", "per402", "per407", 
                 "per414", "per505", "per601", "per603", "per605", "per606")
  left_cols <- c("per103", "per105", "per106", "per107", "per202", "per403", "per404", 
                "per406", "per412", "per413", "per504", "per506", "per701")
  
  data %>%
    mutate(rile_lowe = log((rowSums(select(., all_of(right_cols)) + 0.5)) / 
                          (rowSums(select(., all_of(left_cols)) + 0.5))))
}

# Function to calculate environmental position
calculate_env_position <- function(data) {
  data %>%
    mutate(
      miljo_afhaengig = log((per416 + per501 + 0.5) / (per410 + 0.5))
    )
}

# Function to remove duplicates based on specific columns
remove_duplicates <- function(data, group_cols, value_col) {
  data %>%
    group_by(across(all_of(group_cols))) %>%
    mutate(max_value = max({{value_col}}, na.rm = TRUE)) %>%
    filter({{value_col}} == max_value) %>%
    distinct(across(all_of(group_cols)), .keep_all = TRUE) %>%
    ungroup() %>%
    select(-max_value)
}

# Function to create standard RDD plot
plot_rdd <- function(data, x_var, y_var, group_var, 
                    x_limit = 10, 
                    x_label = "Running Variable", 
                    y_label = "Outcome", 
                    title = "RDD Plot") {
  ggplot(data = subset(data, {{x_var}} <= x_limit)) +
    geom_point(aes(x = {{x_var}}, y = {{y_var}}, shape = {{group_var}}), size = 2) +
    geom_smooth(data = subset(data, {{x_var}} < 0),
                aes(x = {{x_var}}, y = {{y_var}}),
                method = 'lm', formula = y ~ poly(x, 3, raw = TRUE), 
                linetype = 1, color = 'black', size = 1) +
    geom_smooth(data = subset(data, {{x_var}} >= 0),
                aes(x = {{x_var}}, y = {{y_var}}),
                method = 'lm', formula = y ~ poly(x, 3, raw = TRUE), 
                linetype = 1, color = 'black', size = 1) +
    geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
    theme_minimal() +
    labs(title = title, x = x_label, y = y_label) +
    theme(legend.position = 'bottom', legend.title = element_blank())
}
```

## Data Acquisition

```{r data_acquisition}
# Load Manifesto Project Dataset
mp_setapikey(key = "c1f14c8fb84af448bfdb511afd7f415e")
mpds <- mp_maindataset(version = "MPDS2024a")

# Load election and party data
view_election <- read_csv("view_election.csv")
view_party <- read_csv("view_party.csv")

# Filter for European countries
election_european <- filter_european_countries(view_election)
party_european <- filter_european_countries(view_party)
mpds_european <- filter_european_countries(mpds, "countryname")
```

## Data Preprocessing

```{r data_preprocessing}
# Filter for time period after 1960
mpds_european_1960 <- mpds_european %>% filter(date > 196000)
election_european_1960 <- election_european %>% filter(election_date > "1960-01-01")

# Merge PG datasets
pg_election_parties_european <- merge(
  election_european_1960, 
  party_european[, c("party_id", "cmp", "family_id", "family_name", "family_name_short")], 
  by = "party_id", 
  all.x = FALSE, 
  all.y = FALSE
)

# Filter for ecological parties and parliament elections
pg_election_parties_european_eco <- pg_election_parties_european %>%
  filter(family_id == 19 & election_type == "parliament")

# Filter ecological parties in MPDS
mpds_european_1960_eco <- mpds_european_1960 %>% filter(parfam == "10")
```

## Data Corrections

```{r data_corrections}
# Create a correction lookup table
party_corrections <- tribble(
  ~party_id, ~country_name, ~cmp,
  308,  "Switzerland",    43120,
  1781, "Portugal",       35120,
  2254, "Norway",         12110,
  2651, "Austria",        42120,
  196,  "Czech Republic", 82110,
  219,  "Estonia",        83110
)

# Apply corrections
pg_election_parties_european_eco <- pg_election_parties_european_eco %>%
  rows_update(party_corrections, by = c("party_id", "country_name"))
```

## Data Merging

```{r data_merging}
# Merge MPDS and PG data for ecological parties
mpds_pg_1960_eco <- merge(
  mpds_european_1960_eco,
  pg_election_parties_european_eco,
  by.x = c("countryname", "edate", "party"),
  by.y = c("country_name", "election_date", "cmp"), 
  all = TRUE
)

# Select relevant columns
mpds_european_1960_eco_reduced <- mpds_pg_1960_eco %>%
  select(
    countryname, edate, party, oecdmember, eumember, 
    date, partyname, party_name, partyabbrev, party_name_short, 
    parfam, pervote, rile, absseat, seats, party_id, vote_share
  )
```

## Import and Process Threshold Data

```{r threshold_data}
# Import threshold data
samlede_thresholds <- read_delim(
  "Samlede Thresholds.csv", 
  delim = ";", 
  escape_double = FALSE, 
  locale = locale(decimal_mark = ",", grouping_mark = "."), 
  trim_ws = TRUE
) %>% 
  mutate(edate = dmy(edate))  # Convert to date format

# Prepare threshold data for merging
samlede_thresholds_sub <- samlede_thresholds %>%
  select(country, edate, threshold, threshold_lagged)

# Merge threshold data with MPDS data
mpds_european_1960 <- merge(
  mpds_european_1960,
  samlede_thresholds_sub,
  by = c("country", "edate"),
  all.x = FALSE
)

# Calculate average vote share for mainstream parties
mpds_european_1960 <- mpds_european_1960 %>% 
  group_by(party) %>% 
  mutate(avg_pervote_main = mean(pervote, na.rm = TRUE)) %>% 
  ungroup() %>%
  filter(avg_pervote_main >= 10)  # Keep only mainstream parties with >=10% avg
```

## Add Ecological Vote Percentages

```{r eco_votes}
# Import additional ecological vote data
eco_votes_additional <- read_delim(
  "mpds_pg_1960_eco_færdig_tilføjelse_af_ekstra_votes.csv", 
  delim = ";", 
  escape_double = FALSE, 
  col_types = cols(avg_vote_share = col_double()), 
  locale = locale(decimal_mark = ",", grouping_mark = "."), 
  trim_ws = TRUE
) %>%
  mutate(edate = as.Date(edate, format = "%d-%m-%Y")) %>%
  mutate(edate = format(edate, "%Y/%m/%d"))

# Select relevant columns
eco_votes_sub <- eco_votes_additional %>%
  select(
    countryname, edate, pervote_samlet, lagged_pervote_samlet, 
    i_parlament, lagged_i_parlament
  )

# Merge with main dataset
mpds_european_1960_final <- merge(
  mpds_european_1960,
  eco_votes_sub,
  by = c("countryname", "edate"),
  all.x = FALSE
)

# Calculate Lowe's RILE score
mpds_european_1960_final <- calculate_rile_lowe(mpds_european_1960_final)

# Select relevant columns for final dataset
mpds_european_1960_final <- mpds_european_1960_final %>%
  select(
    countryname, edate, country, party, oecdmember, eumember, date, 
    partyname, partyabbrev, parfam, absseat, per410, per416, per501, 
    threshold, threshold_lagged, pervote_samlet, lagged_pervote_samlet, 
    i_parlament, lagged_i_parlament, avg_pervote_main, rile, rile_lowe
  )

# Remove duplicates
mpds_european_1960_final <- remove_duplicates(
  mpds_european_1960_final, 
  c("countryname", "edate", "party"),
  pervote_samlet
)
```

## Calculate Derived Variables

```{r derived_variables}
# Convert vote percentages to numeric
mpds_european_1960_final <- mpds_european_1960_final %>%
  mutate(
    pervote_samlet = as.numeric(pervote_samlet),
    lagged_pervote_samlet = as.numeric(lagged_pervote_samlet),
    
    # Calculate centered vote shares
    centered_pervote_samlet = pervote_samlet - threshold,
    centered_lagged_pervote_samlet = lagged_pervote_samlet - threshold_lagged,
    
    # Calculate dependent environmental variable
    miljo_afhaengig = log((per416 + per501 + 0.5) / (per410 + 0.5))
  )

# Calculate first difference of dependent variable
mpds_european_1960_final <- mpds_european_1960_final %>% 
  arrange(party, edate) %>%
  group_by(party) %>% 
  mutate(miljo_afhaengig_fd = miljo_afhaengig - lag(miljo_afhaengig)) %>% 
  ungroup()

# Create factor variables for parliament status
mpds_european_1960_final <- mpds_european_1960_final %>%
  mutate(
    factor_lagged_i_parlament = factor(
      lagged_i_parlament, 
      levels = c(0, 1), 
      labels = c("Green parties w/o seats", "Green parties w seat(s)")
    ),
    factor_i_parlament = factor(
      i_parlament, 
      levels = c(0, 1), 
      labels = c("Green parties w/o seats", "Green parties w seat(s)")
    )
  )
```

## Visualization and Analysis

```{r visualization}
# Create RDD plot for environmental position
rdd_plot <- plot_rdd(
  data = mpds_european_1960_final,
  x_var = centered_lagged_pervote_samlet,
  y_var = miljo_afhaengig,
  group_var = factor_lagged_i_parlament,
  x_limit = 10,
  x_label = "Green Parties Vote Share (Centered at Threshold)",
  y_label = "Environmental Position",
  title = "RDD Plot: Effect of Parliament Threshold on Environmental Position"
)

print(rdd_plot)

# Create histogram of vote shares by parliament status
hist_plot <- ggplot(
  mpds_european_1960_final, 
  aes(x = centered_lagged_pervote_samlet, fill = factor_lagged_i_parlament)
) +
  geom_histogram(position = "dodge", bins = 20) +
  labs(
    x = "Centered Vote Share", 
    y = "Count", 
    fill = "Parliament Status",
    title = "Distribution of Vote Shares Relative to Threshold"
  ) +
  theme_minimal()

print(hist_plot)
```

## Regression Analysis

```{r regression}
# Simple linear model
model_simple <- lm(
  miljo_afhaengig ~ centered_lagged_pervote_samlet + lagged_i_parlament,
  data = mpds_european_1960_final
)

# Display model results
summary(model_simple)
tidy(model_simple)

# RDD analysis
rdd_result <- rdrobust(
  y = mpds_european_1960_final$miljo_afhaengig,
  x = mpds_european_1960_final$centered_lagged_pervote_samlet,
  c = 0,
  p = 1,
  kernel = "triangular",
  bwselect = "mserd"
)

summary(rdd_result)
```


# Source custom functions
source("gp_rdd_funktioner.R")

# ===== DATA PREPARATION =====
# Clean data - remove missing values for analysis
data_clean <- na.omit(mpds_europæiske_1960_færdig)

# ===== PART 1: BASELINE MODELS =====
# --- 1.1 Base Linear Model ---
model_base <- lm(miljø_afhængig ~ centered_lagged_pervote_samlet * lagged_i_parlament, 
                 data = mpds_europæiske_1960_færdig)

data_used <- as.data.frame(mpds_europæiske_1960_færdig[rownames(model_base$model), ])

# Robust standard errors clustered by party
resultat <- coeftest.cluster_grøn(data = data_used,
                             fm = model_base,
                             cluster1 = "party")
print(resultat)

# Robust standard errors clustered by party and election date
summary_model <- summary.cluster_grøn(obj = model_base, 
                                 data = data_used, 
                                 cluster1 = "party", 
                                 cluster2 = "edate")
print(summary_model)

# --- 1.2 Instrumental Variable Approach ---
model_iv <- ivreg(miljø_afhængig ~ lagged_i_parlament | centered_lagged_pervote_samlet, 
                  data = mpds_europæiske_1960_færdig)
summary(model_iv, diagnostics = TRUE)

# --- 1.3 RDD Base Analysis ---
rd.multic_grøn <- rd.base_grøn(
  data = mpds_europæiske_1960_færdig,
  force.var = 'centered_lagged_pervote_samlet',
  yvar = 'miljø_afhængig',
  seat.identifier = 'factor_lagged_i_parlament',
  fixed.effects = 'country',
  clust1 = 'party',
  clust2 = 'edate',
  polynomials = c(1, 2, 3, 4),
  bws = NULL
)
print(rd.multic_grøn)

# ===== PART 2: COMPREHENSIVE RDD ANALYSIS =====
# --- 2.1 Configuration ---
# Bandwidths to test
bw_list <- c(1, 1.5, 2, 2.5, 3)
# Polynomial orders to test
polynomials <- c(1, 2, 3, 4)
# Empty list for results
all_results <- list()

# --- 2.2 Function for RDD Analysis ---
run_rdrobust_analysis <- function(data, p, bw = NULL, interaction = FALSE) {
  # Base covariates
  base_covs <- cbind(
    data$country,
    data$edate,
    data$lagged_i_parlament
  )
  
  # Add interaction term if requested
  if(interaction) {
    covs <- cbind(
      base_covs,
      data$rile_lowe,
      data$rile_lowe * data$lagged_i_parlament
    )
  } else {
    covs <- base_covs
  }
  
  # Run RD analysis
  rd <- rdrobust(
    y = data$miljø_afhængig,
    x = data$centered_lagged_pervote_samlet,
    c = 0,
    p = p,
    h = bw,
    covs = covs
  )
  
  return(rd)
}

# --- 2.3 Run Analyses for Different Specifications ---
for (p in polynomials) {
  if (p <= 2) {
    # Local polynomial with fixed bandwidths
    for (bw in bw_list) {
      # Original model
      rd_original <- run_rdrobust_analysis(data_clean, p, bw, interaction = FALSE)
      
      # Model with interaction
      rd_interaction <- run_rdrobust_analysis(data_clean, p, bw, interaction = TRUE)
      
      # Compile results
      tmp <- data.frame(
        Model = c("Original", "With Interaction"),
        Bandwidth = bw,
        Polynomial = p,
        LATE = formatC(c(rd_original$Estimate[1], rd_interaction$Estimate[1]), format = "f", digits = 4),
        StdErr = formatC(c(rd_original$se[1], rd_interaction$se[1]), format = "f", digits = 4),
        p_value = formatC(c(rd_original$pv[1], rd_interaction$pv[1]), format = "f", digits = 4),
        N_left_of_c = c(rd_original$N_h[1], rd_interaction$N_h[1]),
        N_right_of_c = c(rd_original$N_h[2], rd_interaction$N_h[2])
      )
      
      # Add significance stars
      tmp$p_value_star <- paste0(
        tmp$p_value,
        ifelse(as.numeric(tmp$p_value) < 0.01, "***",
               ifelse(as.numeric(tmp$p_value) < 0.05, "**",
                      ifelse(as.numeric(tmp$p_value) < 0.1, "*", "")))
      )
      
      all_results[[paste0("p", p, "_bw", bw)]] <- tmp
    }
  } else {
    # Global polynomial (automatically selected bandwidth)
    rd_original <- run_rdrobust_analysis(data_clean, p, NULL, interaction = FALSE)
    rd_interaction <- run_rdrobust_analysis(data_clean, p, NULL, interaction = TRUE)
    
    tmp <- data.frame(
      Model = c("Original", "With Interaction"),
      Bandwidth = NA,
      Polynomial = p,
      LATE = formatC(c(rd_original$Estimate[1], rd_interaction$Estimate[1]), format = "f", digits = 4),
      StdErr = formatC(c(rd_original$se[1], rd_interaction$se[1]), format = "f", digits = 4),
      p_value = formatC(c(rd_original$pv[1], rd_interaction$pv[1]), format = "f", digits = 4),
      N_left_of_c = c(rd_original$N_h[1], rd_interaction$N_h[1]),
      N_right_of_c = c(rd_original$N_h[2], rd_interaction$N_h[2])
    )
    
    # Add significance stars
    tmp$p_value_star <- paste0(
      tmp$p_value,
      ifelse(as.numeric(tmp$p_value) < 0.01, "***",
             ifelse(as.numeric(tmp$p_value) < 0.05, "**",
                    ifelse(as.numeric(tmp$p_value) < 0.1, "*", "")))
    )
    
    all_results[[paste0("p", p, "_global")]] <- tmp
  }
}

# Combine results
results_df <- do.call(rbind, all_results)
print(results_df)

# ===== PART 3: SUBSAMPLE ANALYSIS FOR LEFT PARTIES =====
# Filter data for left-oriented parties (assuming lower rile_lowe = more left-oriented)
left_parties <- data_clean[data_clean$rile_lowe < median(data_clean$rile_lowe, na.rm = TRUE), ]

# Run RDD on left parties subsample
rd_left_only <- rdrobust(
  y = left_parties$miljø_afhængig,
  x = left_parties$centered_lagged_pervote_samlet,
  c = 0,
  p = 2,
  h = 2,
  covs = cbind(
    left_parties$country,
    left_parties$edate,
    left_parties$lagged_i_parlament
  )
)
summary(rd_left_only)

# ===== PART 4: ROBUSTNESS CHECKS =====
# --- 4.1 Placebo Tests ---
placebo_cutpoints <- c(2, 5, 7)
placebo_results <- list()

for (cp in placebo_cutpoints) {
  rd <- rdrobust(
    y = data_clean$miljø_afhængig,
    x = data_clean$centered_lagged_pervote_samlet,
    c = cp,
    p = 1,
    h = 2,
    covs = cbind(
      data_clean$country,
      data_clean$edate,
      data_clean$lagged_i_parlament
    )
  )
  
  placebo_results[[paste0("cp_", cp)]] <- data.frame(
    cutoff = cp,
    estimate = rd$Estimate[1],
    std_err = rd$se[1],
    p_value = rd$pv[1],
    n_left = rd$N_h[1],
    n_right = rd$N_h[2]
  )
}

# Combine placebo results
placebo_df <- do.call(rbind, placebo_results)
print(placebo_df)

# --- 4.2 McCrary Density Test ---
density_test <- rddensity(X = mpds_europæiske_1960_færdig$centered_lagged_pervote_samlet, c = 0)
summary(density_test)

# --- 4.3 Bandwidth Selection ---
bw_selection <- rdbwselect(
  y = mpds_europæiske_1960_færdig$miljø_afhængig, 
  x = mpds_europæiske_1960_færdig$centered_lagged_pervote_samlet, 
  c = 0
)
summary(bw_selection)

# ===== PART 5: VISUALIZATIONS =====
# --- 5.1 Main RDD Plot ---
p1_grøn <- jump.plot_grøn(
  data = subset(mpds_europæiske_1960_færdig, centered_lagged_pervote_samlet <= 10),
  force.var = 'centered_lagged_pervote_samlet',
  yvar = 'miljø_afhængig',
  seat.identifier = 'factor_lagged_i_parlament',
  polynomial = 3
)
print(p1_grøn)

# --- 5.2 Focused RDD Plot (Zoomed to [-2, 2]) ---
jump.plot.cutoff <- function(data, force.var, yvar, seat.identifier, polynomial) {
  # Select relevant variables and remove NAs
  data <- data[, c(force.var, yvar, seat.identifier)]
  data <- na.omit(data)
  
  p <- ggplot() +
    geom_point(data = data,
               aes_string(x = force.var, y = yvar, shape = seat.identifier),
               size = 2) +
    geom_smooth(data = subset(data, data[, force.var] < 0),
                aes_string(x = force.var, y = yvar),
                method = 'lm',
                formula = y ~ poly(x, polynomial, raw = TRUE),
                linetype = 1,
                color = 'black',
                size = 1) +
    geom_smooth(data = subset(data, data[, force.var] >= 0),
                aes_string(x = force.var, y = yvar),
                method = 'lm',
                formula = y ~ poly(x, polynomial, raw = TRUE),
                linetype = 1,
                color = 'black',
                size = 1) +
    scale_x_continuous(name = 'Vote Share of Green Parties',
                       limits = c(-2, 2),
                       breaks = seq(-2, 2, 0.5)) +
    scale_y_continuous(name = 'Focus on Environment',
                       limits = c(-8, 8),
                       breaks = seq(-8, 8, 4)) +
    scale_shape_manual(values = c(1, 19),
                       labels = c('Green Parties w/o seats', 'Green Parties w seat(s)')) +
    geom_vline(xintercept = 0, linetype = 2, size = 0.6) +
    theme_minimal() +
    theme(legend.position = 'bottom', legend.title = element_blank())
  
  return(p)
}

p_cutoff <- jump.plot.cutoff(
  data = subset(mpds_europæiske_1960_færdig, 
                centered_lagged_pervote_samlet >= -2 & centered_lagged_pervote_samlet <= 2),
  force.var = 'centered_lagged_pervote_samlet',
  yvar = 'miljø_afhængig',
  seat.identifier = 'factor_lagged_i_parlament',
  polynomial = 3
)
print(p_cutoff)

# --- 5.3 Interaction Plot ---
plot_interaction <- ggplot(data_clean, 
                          aes(x = centered_lagged_pervote_samlet, 
                              y = miljø_afhængig,
                              color = factor(lagged_i_parlament))) +
  geom_point(alpha = 0.6) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(
    title = "Interaction between Parliament Status and Vote Share",
    x = "Vote Percentage (centered around threshold)",
    y = "Environmental Policy Focus",
    color = "In Parliament (lagged)"
  ) +
  theme_minimal()
print(plot_interaction)

# --- 5.4 Outcome Distribution ---
hist_plot <- ggplot(mpds_europæiske_1960_færdig, aes(x = miljø_afhængig)) +
  geom_histogram(binwidth = 0.1, fill = "steelblue", color = "black") +
  labs(title = "Distribution of Outcome Variable", 
       x = "Environmental Policy Focus", 
       y = "Number of Observations") +
  theme_minimal()
print(hist_plot)

# --- 5.5 Density Plot ---
rddensity_plot <- rdplotdensity(
  density_test, 
  X = mpds_europæiske_1960_færdig$centered_lagged_pervote_samlet
)

density_hist <- ggplot(mpds_europæiske_1960_færdig, aes(x=centered_lagged_pervote_samlet)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +
  labs(title = "Distribution of Running Variable",
       x = "Vote Share (centered)",
       y = "Density") +
  theme_minimal()
print(density_hist)

# --- 5.6 Placebo Visualization ---
# Example for one placebo cutoff
placebo_cutoff <- 7

# Create indicator for 'left' vs 'right' of cutpoint
data_clean$D <- ifelse(data_clean$centered_lagged_pervote_samlet < placebo_cutoff, 0, 1)

placebo_plot <- ggplot(data_clean, 
                      aes(x = centered_lagged_pervote_samlet, y = miljø_afhængig)) +
  geom_point(alpha = 0.4) +
  geom_vline(xintercept = placebo_cutoff, color = "red", linetype = "dashed") +
  stat_smooth(
    data = subset(data_clean, D == 0),
    method = "lm",
    formula = y ~ poly(x, 1),
    color = "blue"
  ) +
  stat_smooth(
    data = subset(data_clean, D == 1),
    method = "lm",
    formula = y ~ poly(x, 1),
    color = "blue"
  ) +
  theme_minimal() +
  labs(title = paste0("Placebo Check at x=", placebo_cutoff),
       x = "Vote Share (centered)",
       y = "Environmental Policy Focus")
print(placebo_plot)

# ===== PART 6: ADDITIONAL RDD APPROACHES =====
# --- 6.1 RDD with rdd package ---
rdd_data <- rdd_data(
  y = mpds_europæiske_1960_færdig$miljø_afhængig,
  x = mpds_europæiske_1960_færdig$centered_lagged_pervote_samlet,
  cutpoint = 0
)

rdd_model <- rdd_reg_lm(rdd_object = rdd_data)
summary(rdd_model)
plot(rdd_model)

# --- 6.2 Simple Linear Models ---
# Overall sample
reg <- lm(miljø_afhængig ~ factor_lagged_i_parlament + centered_lagged_pervote_samlet, 
          data = mpds_europæiske_1960_færdig, 
          na.action = na.omit)

stargazer(reg, 
          type = "text", 
          dep.var.labels = ("Environmental Policy Focus"),
          column.labels = c(""),
          covariate.labels = c("Treatment", "Green Parties Vote Share"),
          omit.stat = "all", 
          digits = 2)

# Left-wing parties subsample
mpds_venstre <- subset(mpds_europæiske_1960_færdig, rile_lowe < 0)

reg_left <- lm(miljø_afhængig ~ factor_lagged_i_parlament + centered_lagged_pervote_samlet, 
              data = mpds_venstre, 
              na.action = na.omit)

stargazer(reg_left, 
          type = "text", 
          dep.var.labels = ("Environmental Policy Focus"),
          column.labels = c(""),
          covariate.labels = c("Treatment", "Green Parties Vote Share"),
          omit.stat = "all", 
          digits = 2)