```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# 1. Setup and Data Preparation
```{r Load af data}
final_dataset <- readRDS("final_dataset_publisering.rds")
```



## 1.1 Package Installation and Loading

```{r package_installation}
# Install pacman if not already installed
if (!require("pacman")) install.packages("pacman")

pacman::p_load(
  # Data manipulation
  dplyr, tidyr, magrittr, purrr, data.table, readr, lubridate, quantreg, MASS,
  
  # Visualization
  ggplot2, patchwork, scales, RColorBrewer, gridExtra, ggridges, corrplot, ggh4x, modelsummary, kableExtra, UpSetR, reshape2, viridis, plotly,
  
  # Statistical analysis
  rdd, rddtools, rddensity, rdrobust, rdlocrand, AER, ivreg,
  lmtest, sandwich, stargazer, broom, memisc, strucchange, plm, fixest,
  
  # Missing data analysis
  naniar,
  
  # Specific data sources
  manifestoR
)

# Load custom RDD functions if available
if (file.exists("gp_rdd_funktioner.R")) {
  source("gp_rdd_funktioner.R")
}

if (file.exists("coefficient_stability_plots.R")) {
  source("coefficient_stability_plots.R")
}

if (file.exists("placebo_tests.R")) {
  source("placebo_tests.R")
} 
```

## 1.2 Helper Functions

```{r helper_functions}
# Cluster-robust SEs need enough clusters to be trustworthy (conventional rule of
# thumb: 20-30+); with fewer, they can become anti-conservative (artificially
# small), inflating apparent significance. Reports the count and warns if thin,
# for any rdrobust() call clustered on a single variable.
check_cluster_count <- function(cluster_vec, label, min_clusters = 20) {
  n <- length(unique(cluster_vec))
  cat(label, "- unique clusters:", n,
      if (n < min_clusters) paste0(" (BELOW ", min_clusters, " -- cluster-robust SE may be unreliable)") else "",
      "\n")
  if (n < min_clusters) {
    warning(paste0(label, ": only ", n, " unique clusters (< ", min_clusters,
                   ") -- do not lean on this model's significance stars alone."))
  }
  invisible(n)
}

# rdrobust() only actually uses observations within its selected bandwidth (bws
# columns: 1 = left, 2 = right, same convention already used elsewhere in this
# file for the reported Bandwidth). Checking cluster counts on the full input
# vector would overstate how many clusters the model actually estimated from.
check_rdrobust_cluster_count <- function(rdrobust_model, data, running_var, cluster_var, label) {
  bw_left <- rdrobust_model$bws[1, 1]
  bw_right <- rdrobust_model$bws[1, 2]
  x <- data[[running_var]]
  in_bw <- (x < 0 & x >= -bw_left) | (x >= 0 & x <= bw_right)
  check_cluster_count(data[[cluster_var]][in_bw], label)
}

# Function to filter European countries
filter_european_countries <- function(data, country_col = "country_name") {
  european_countries <- c(
    "Austria", "Bulgaria", "Croatia", "Czech Republic", "Denmark", 
    "Estonia", "Finland", "Germany", "Greece", "Ireland", "Italy", 
    "Latvia", "Luxembourg", "Netherlands", "Norway", "Poland", 
    "Portugal", "Romania", "Slovakia", "Slovenia", "Spain", 
    "Sweden", "Switzerland"
  )
  
  filter(data, !!sym(country_col) %in% european_countries)
}

# Funktion til at udføre robusthedstest med forskellige båndbredder
run_rdd_robustness <- function(data,
                              outcome_var = "miljø_afhængig",
                              running_var = "centered_lagged_pervote_samlet",
                              bw_list = c(1, 1.5, 2, 2.5, 3),
                              polynomials = c(1, 2, 3, 4),
                              cutpoint = 0,
                              covariates = NULL,
                              cluster_var = "country_election_id",
                              group_label = "") {

  # Tom liste til resultater
  all_results <- list()

  # Standard errors are clustered by country-election (default) since the Green
  # party running variable/treatment is identical for every mainstream party
  # observed in the same country-election, not independent across observations.
  cluster_vec <- if (!is.null(cluster_var) && cluster_var %in% names(data)) data[[cluster_var]] else NULL
  
  # Håndtering af kovariater
  if (!is.null(covariates)) {
    # Opret kovariat-matrix på forhånd
    covs_matrix <- NULL
    if (length(covariates) > 0) {
      # Forsøg at bygge kovariat-matrix manuelt
      covs_list <- list()
      for (i in 1:length(covariates)) {
        col_name <- covariates[i]
        if (col_name %in% names(data)) {
          covs_list[[i]] <- data[[col_name]]
        } else {
          warning(paste("Kolonne", col_name, "findes ikke i datasættet."))
          covs_list[[i]] <- NULL
        }
      }
      # Fjern NULL værdier
      covs_list <- covs_list[!sapply(covs_list, is.null)]
      
      # Hvis der er nogen kovariater tilbage, lav en matrix
      if (length(covs_list) > 0) {
        covs_matrix <- do.call(cbind, covs_list)
      }
    }
  } else {
    covs_matrix <- NULL
  }
  
  # Loop over polynomier
  for (p in polynomials) {
    
    # HVIS p <= 2, laver den 'ikke-parametrisk' med faste båndbredder
    if (p <= 2) {
      
      # Loop over båndbredder
      for (bw in bw_list) {
        # Prøv at køre rdrobust med fejlhåndtering
        tryCatch({
          # Kør rdrobust uden kovariater
          if (is.null(covs_matrix)) {
            rd <- rdrobust(
              y = data[[outcome_var]],
              x = data[[running_var]],
              c = cutpoint,
              p = p,
              h = bw,
              cluster = cluster_vec
            )
          } else {
            # Kør rdrobust med kovariater
            rd <- rdrobust(
              y = data[[outcome_var]],
              x = data[[running_var]],
              c = cutpoint,
              p = p,
              h = bw,
              covs = covs_matrix,
              cluster = cluster_vec
            )
          }
          
          # Gem KUN conventional-estimatet: [1]
          tmp <- data.frame(
            Bandwidth    = bw,
            Polynomial   = p,
            LATE         = formatC(rd$Estimate[1], format = "f", digits = 4),
            StdErr       = formatC(rd$se[1], format = "f", digits = 4),
            p_value      = formatC(rd$pv[1], format = "f", digits = 4),
            N_left_of_c  = rd$N_h[1],
            N_right_of_c = rd$N_h[2]
          )
          
          # Tilføj en kolonne med p-værdi-stjerner
          tmp$p_value_star <- paste0(
            tmp$p_value,
            ifelse(as.numeric(tmp$p_value) < 0.01, "***",
                   ifelse(as.numeric(tmp$p_value) < 0.05, "**",
                          ifelse(as.numeric(tmp$p_value) < 0.1, "*", "")))
          )
          
          # Læg i listen over resultater
          all_results[[paste0("p", p, "_bw", bw)]] <- tmp
          
        }, error = function(e) {
          warning(paste("Fejl ved kørsel af rdrobust med p =", p, "og bw =", bw, ":", e$message))
        })
      }
      
    } else {
      # HVIS p > 2, laver den "global" og sætter h = NULL (eller en meget stor værdi)
      tryCatch({
        # Kør rdrobust uden kovariater
        if (is.null(covs_matrix)) {
          rd <- rdrobust(
            y = data[[outcome_var]],
            x = data[[running_var]],
            c = cutpoint,
            p = p,
            h = NULL,   # lader rdrobust selv vælge båndbredde
            cluster = cluster_vec
          )
        } else {
          # Kør rdrobust med kovariater
          rd <- rdrobust(
            y = data[[outcome_var]],
            x = data[[running_var]],
            c = cutpoint,
            p = p,
            h = NULL,   # lader rdrobust selv vælge båndbredde
            covs = covs_matrix,
            cluster = cluster_vec
          )
        }
        
        # Gem KUN conventional-estimatet: [1]
        tmp <- data.frame(
          Bandwidth    = NA,  # "Global" => ingen fastsat h
          Polynomial   = p,
          LATE         = formatC(rd$Estimate[1], format = "f", digits = 4),
          StdErr       = formatC(rd$se[1], format = "f", digits = 4),
          p_value      = formatC(rd$pv[1], format = "f", digits = 4),
          N_left_of_c  = rd$N_h[1],
          N_right_of_c = rd$N_h[2]
        )
        
        # Tilføj en kolonne med p-værdi-stjerner
        tmp$p_value_star <- paste0(
          tmp$p_value,
          ifelse(as.numeric(tmp$p_value) < 0.01, "***",
                 ifelse(as.numeric(tmp$p_value) < 0.05, "**",
                        ifelse(as.numeric(tmp$p_value) < 0.1, "*", "")))
        )
        
        # Læg i listen
        all_results[[paste0("p", p, "_global")]] <- tmp
        
      }, error = function(e) {
        warning(paste("Fejl ved kørsel af rdrobust med p =", p, "og global båndbredde:", e$message))
      })
    }
  }
  
  if (length(all_results) > 0) {
    results_df <- do.call(rbind, all_results)
    
    # Tilføj en kolonne med gruppelabel, hvis angivet
    if (group_label != "") {
      results_df$Group <- group_label
    }
    
    return(results_df)
  } else {
    warning("Ingen resultater produceret. Tjek data og parametre.")
    return(NULL)
  }
}

# Function to calculate Lowe's RILE score
calculate_rile_lowe <- function(data) {
  right_cols <- c("per104", "per201", "per203", "per305", "per401", "per402", "per407", 
                 "per414", "per505", "per601", "per603", "per605", "per606")
  left_cols <- c("per103", "per105", "per106", "per107", "per202", "per403", "per404", 
                "per406", "per412", "per413", "per504", "per506", "per701")
  
  # Debug: Identify missing columns
  missing_right <- right_cols[!right_cols %in% names(data)]
  missing_left <- left_cols[!left_cols %in% names(data)]
  print(paste("Missing right columns:", paste(missing_right, collapse=", ")))
  print(paste("Missing left columns:", paste(missing_left, collapse=", ")))
  
  # Filter to only include columns that exist in the dataset
  right_cols_exist <- right_cols[right_cols %in% names(data)]
  left_cols_exist <- left_cols[left_cols %in% names(data)]
  
  # Calculate RILE score
  data %>%
    mutate(rile_lowe = log((rowSums(dplyr::select(., dplyr::all_of(right_cols_exist)) + 0.5)) / 
                          (rowSums(dplyr::select(., dplyr::all_of(left_cols_exist)) + 0.5))))
}

# Function to remove duplicates based on specific columns
remove_duplicates <- function(data, group_cols, value_col) {
  data %>%
    dplyr::group_by(dplyr::across(dplyr::all_of(group_cols))) %>%
    dplyr::mutate(max_value = max({{value_col}}, na.rm = TRUE)) %>%
    dplyr::filter({{value_col}} == max_value) %>%
    dplyr::distinct(dplyr::across(dplyr::all_of(group_cols)), .keep_all = TRUE) %>%
    dplyr::ungroup() %>%
    dplyr::select(-"max_value")  # Change to this or the alternate option below
}

# Function to create standard RDD plot
plot_rdd <- function(data, x_var, y_var, group_var, 
                    x_limit = 10, 
                    x_label = "Treatment Variable", 
                    y_label = "Result", 
                    title = "RDD Plot") {
  # Ensure x_var, y_var, and group_var are treated as strings (column names)
  ggplot(data = subset(data, data[[x_var]] <= x_limit)) +
    geom_point(aes(x = .data[[x_var]], y = .data[[y_var]], shape = .data[[group_var]]), size = 2) +
    geom_smooth(data = subset(data, data[[x_var]] < 0),
                aes(x = .data[[x_var]], y = .data[[y_var]]),
                method = 'lm', formula = y ~ poly(x, 3, raw = TRUE), 
                linetype = 1, color = 'black', size = 1) +
    geom_smooth(data = subset(data, data[[x_var]] >= 0),
                aes(x = .data[[x_var]], y = .data[[y_var]]),
                method = 'lm', formula = y ~ poly(x, 3, raw = TRUE), 
                linetype = 1, color = 'black', size = 1) +
    scale_shape_manual(values = c(1, 16)) +  # 1 = tom cirkel, 16 = fyldt cirkel
    geom_vline(xintercept = 0, linetype = 2, size = .6) +
    xlim(-5, x_limit) +  # Sætter x-aksens grænser
    theme_minimal() +
    labs(title = title, x = x_label, y = y_label) +
    theme(legend.position = 'bottom', legend.title = element_blank())
}
```


```{r h1_analysis}
# Opret først hovedmappen Robusthedstests, hvis den ikke allerede eksisterer
dir.create("Publisering Analyse", showWarnings = FALSE)

# Opret derefter undermappen H4 tests - Appendiks
dir.create("Publisering Analyse/H1", showWarnings = FALSE)

# 0. For H1 analysis that examines Green Party parliamentary entry effect ----------------
h1_analysis_data <- final_dataset[complete.cases(final_dataset[, c("miljø_afhængig",
                                                                 "centered_lagged_pervote_samlet",
                                                                 "lagged_i_parlament",
                                                                 "country",
                                                                 "edate",
                                                                 "country_election_id")]), ]

# Check how many observations there are now
nrow(h1_analysis_data)

# Compare with original and clean_data
#cat("Original rows in final_dataset:", nrow(final_dataset), "\n")
#cat("Rows in h1_analysis_data:", nrow(h1_analysis_data), "\n")
#cat("Rows in clean_data:", nrow(clean_data), "\n")

# Compare with original and clean_data
#cat("Original rows in final_dataset:", nrow(final_dataset), "\n")
#cat("Rows in h1_analysis_data:", nrow(h1_analysis_data), "\n")
#cat("Rows in clean_data:", nrow(clean_data), "\n")

# 1. VISUAL INSPECTION OF THE DISCONTINUITY ----------------

# Create RDD plot 
h1_plot_rdd <- plot_rdd(
  data = h1_analysis_data,
  x_var = "centered_lagged_pervote_samlet",
  y_var = "miljø_afhængig",
  group_var = "factor_lagged_i_parlament",
  x_limit = 10,
  x_label = "Green Party Vote Share (Centered on Cut-off)",
  y_label = "Environmental Focus",
  title = "Effect of Green Party Entry on Mainstream Environmental Focus"
)

# Save the plot
ggsave("Publisering Analyse/H1/h1_rdd_plot.png", h1_plot_rdd, width = 10, height = 6, dpi = 300)

# 2. RDD ESTIMATION ----------------

# Main RDD estimation with optimal bandwidth
h1_rdd <- rdrobust(
  y = h1_analysis_data$miljø_afhængig,
  x = h1_analysis_data$centered_lagged_pervote_samlet,
  c = 0,
  p = 1,  # linear polynomial
  kernel = "triangular",
  bwselect = "mserd",  # MSE-optimal bandwidth
  # Cluster by country-election: the same Green party running variable/treatment
  # value is shared by every mainstream party observed in the same election.
  cluster = h1_analysis_data$country_election_id
)
check_rdrobust_cluster_count(h1_rdd, h1_analysis_data, "centered_lagged_pervote_samlet",
                              "country_election_id", "H1 main rdrobust")

# Print summary
summary_h1 <- summary(h1_rdd)

# Opret tabel direkte fra h1_rdd objektet. Reports both the Conventional estimate
# (index 1: naive point estimate + naive SE) and the Robust one (index 3: Calonico,
# Cattaneo & Titiunik 2014's bias-corrected estimate + robust SE) -- the latter is
# the one with valid coverage when using an MSE-optimal bandwidth (as we do here),
# since the conventional SE does not account for the bias this bandwidth choice
# introduces. Reporting both rather than only the theoretically preferred one.
main_results <- data.frame(
  Outcome = "Climate Position",
  Bandwidth = round(h1_rdd$bws[1, 1], 3),
  LATE = round(h1_rdd$Estimate[1], 3),
  StdError = round(h1_rdd$se[1], 3),
  pvalue = round(h1_rdd$pv[1], 3),
  CI_Lower = round(h1_rdd$ci[1, 1], 3),
  CI_Upper = round(h1_rdd$ci[1, 2], 3),
  LATE_robust = round(h1_rdd$Estimate[3], 3),
  StdError_robust = round(h1_rdd$se[3], 3),
  pvalue_robust = round(h1_rdd$pv[3], 3),
  CI_Lower_robust = round(h1_rdd$ci[3, 1], 3),
  CI_Upper_robust = round(h1_rdd$ci[3, 2], 3)
)

main_results_table <- knitr::kable(main_results,
                                  caption = "Main RDD Results for H1 (Conventional and Robust bias-corrected, Calonico/Cattaneo/Titiunik 2014)",
                                  col.names = c("Outcome Variable", "Bandwidth", "LATE", "Std. Error",
                                               "p-value", "95% CI Lower", "95% CI Upper",
                                               "LATE (Robust)", "St. Err. (Robust)", "p-value (Robust)",
                                               "95% CI Lower (Robust)", "95% CI Upper (Robust)"))

writeLines(main_results_table, file.path(getwd(), "Publisering Analyse/H1/Publisering h1_main_results.md"))
print(main_results_table)
write.csv(main_results_table, "Publisering Analyse/H1/Publisering h1_main_results.csv", row.names = FALSE)  


# 3. ROBUSTNESS CHECKS ----------------

# 3.1 Different Bandwidths and Polynomial Orders ----------

results_df_h1 <- run_rdd_robustness(
  data = h1_analysis_data,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3, 3.5, 4),
  polynomials = c(1, 2, 3, 4),
  covariates = c("country", "edate"),
  group_label = "H1"
)

print(results_df_h1)
selected_columns <- c("Group", "Polynomial", "Bandwidth", "LATE", "p_value", "StdErr", "N_left_of_c", "N_right_of_c")
subset_df <- results_df_h1[, selected_columns]
robustness_table_h1 <- knitr::kable(subset_df, 
                               caption = "RDD Estimates Across Different Specifications",
                               col.names = c("Group", "Polynomial", "Bandwidth", "LATE","p-value", "Std. Error", 
                                              "N Left", "N Right"))

writeLines(robustness_table_h1, file.path(getwd(), "Publisering Analyse/H1/Publisering h1_robustness_table.md"))
print(robustness_table_h1)
write.csv(subset_df, "Publisering Analyse/H1/Publisering h1_robustness_table.csv", row.names = FALSE)


# 3.2 Looking at different DV's --------------------
#environment (positive) per501
results_df_h1_per501 <- run_rdd_robustness(
  data = h1_analysis_data,
  outcome_var = "per501",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3),
  polynomials = c(1, 2, 3, 4),
  covariates = c("country", "edate"),
  group_label = "H1"
)

print(results_df_h1_per501)
selected_columns <- c("Group", "Polynomial", "Bandwidth", "LATE", "p_value", "StdErr", "N_left_of_c", "N_right_of_c")
subset_df <- results_df_h1_per501[, selected_columns]
robustness_table_per501 <- knitr::kable(subset_df, 
                               caption = "RDD Estimates Across Different Specifications",
                               col.names = c("Group", "Polynomial", "Bandwidth", "LATE","p-value", "Std. Error", 
                                              "N Left", "N Right"))

writeLines(robustness_table_per501, file.path(getwd(), "Publisering Analyse/H1/Publisering h1_robustness_table_per501.md"))
print(robustness_table_per501)
write.csv(subset_df, "Publisering Analyse/H1/Publisering h1_robustness_table_per501.csv", row.names = FALSE)

#Sustainability (positive) per416_2
results_df_h1_per416_2 <- run_rdd_robustness(
  data = h1_analysis_data,
  outcome_var = "per416_2",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3),
  polynomials = c(1, 2, 3, 4),
  covariates = c("country", "edate"),
  group_label = "H1"
)

print(results_df_h1_per416_2)
selected_columns <- c("Group", "Polynomial", "Bandwidth", "LATE", "p_value", "StdErr", "N_left_of_c", "N_right_of_c")
subset_df <- results_df_h1_per416_2[, selected_columns]
robustness_table_per416_2 <- knitr::kable(subset_df, 
                               caption = "RDD Estimates Across Different Specifications",
                               col.names = c("Group", "Polynomial", "Bandwidth", "LATE","p-value", "Std. Error", 
                                              "N Left", "N Right"))

writeLines(robustness_table_per416_2, file.path(getwd(), "Publisering Analyse/H1/Publisering h1_robustness_table_per416_2.md"))
print(robustness_table_per416_2)
write.csv(subset_df, "Publisering Analyse/H1/Publisering h1_robustness_table_per416_2.csv", row.names = FALSE)

# 3.3 Difference between SPD and CDU in Germany ---------------------
# 1. Create Subsets for Germany
# Social Democrats
data_SPD <- subset(h1_analysis_data, country == 41 & party == 41320)

# Christian Democratic Union
data_CDU <- subset(h1_analysis_data, country == 41 & party == 41521)

# 2. Run RDD for Social Democrats
results_SPD <- run_rdd_robustness(
  data = data_SPD,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3),
  polynomials = c(1),
  covariates = c("edate"),
  group_label = "Germany - SPD"
)

# 3. Run RDD for Venstre
results_CDU <- run_rdd_robustness(
  data = data_CDU,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
   bw_list = c(1, 1.5, 2, 2.5, 3),  
  polynomials = c(1),
  covariates = c("edate"),
  group_label = "Germany - CDU"
)

# 4. Compare
print("--- Social Democrats Results ---")
print(results_SPD)
print("--- CDU Results ---")
print(results_CDU)

# 3.4 Germany ----------------------------
# Extract SPD Data (Germany 2005)
spd_data_2005 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41320 & 
                   format(as.Date(edate), "%Y") == "2005") 

# Extract CDU/CSU Data (Germany 2005)
cdu_data_2005 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41521 & 
                   format(as.Date(edate), "%Y") == "2005") 

# --- STEP 3: Get the Scores ---
# We take the first value found to avoid potential duplicates
spd_score_2005 <- spd_data_2005$miljø_afhængig[1]
cdu_score_2005 <- cdu_data_2005$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
german_gap_2005 <- abs(spd_score_2005 - cdu_score_2005)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_ge_2005 <- (my_late_estimate / german_gap_2005) * 100

# --- STEP 6: Print the Result ---
print(paste("SPD Score (DE 2005):    ", round(spd_score_2005, 3)))
print(paste("CDU/CSU Score (DE 2005):", round(cdu_score_2005, 3)))
print(paste("The German Gap:         ", round(german_gap_2005, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_ge_2005, 1), "% of the gap between the SPD and CDU."))

# --- STEP 2: Select the Election Year ---

# Extract SPD Data (Germany 2009)
spd_data_2009 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41320 & 
                   format(as.Date(edate), "%Y") == "2009") 

# Extract CDU/CSU Data (Germany 2009)
cdu_data_2009 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41521 & 
                   format(as.Date(edate), "%Y") == "2009") 

# --- STEP 3: Get the Scores ---
# We take the first value found to avoid potential duplicates
spd_score_2009 <- spd_data_2009$miljø_afhængig[1]
cdu_score_2009 <- cdu_data_2009$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
german_gap_2009 <- abs(spd_score_2009 - cdu_score_2009)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_ge_2009 <- (my_late_estimate / german_gap_2009) * 100

# --- STEP 6: Print the Result ---
print(paste("SPD Score (DE 2009):    ", round(spd_score_2009, 3)))
print(paste("CDU/CSU Score (DE 2009):", round(cdu_score_2009, 3)))
print(paste("The German Gap:         ", round(german_gap_2009, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_ge_2009, 1), "% of the gap between the SPD and CDU."))

# Extract SPD Data (Germany 2013)
spd_data_2013 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41320 & 
                   format(as.Date(edate), "%Y") == "2013") 

# Extract CDU/CSU Data (Germany 2013)
cdu_data_2013 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41521 & 
                   format(as.Date(edate), "%Y") == "2013") 

# --- Germany 2013 ---
# We take the first value found to avoid potential duplicates
spd_score_2013 <- spd_data_2013$miljø_afhængig[1]
cdu_score_2013 <- cdu_data_2013$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
german_gap_2013 <- abs(spd_score_2013 - cdu_score_2013)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_ge_2013 <- (my_late_estimate / german_gap_2013) * 100

# --- STEP 6: Print the Result ---
print(paste("SPD Score (DE 2013):    ", round(spd_score_2013, 3)))
print(paste("CDU/CSU Score (DE 2013):", round(cdu_score_2013, 3)))
print(paste("The German Gap:         ", round(german_gap_2013, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_ge_2013, 1), "% of the gap between the SPD and CDU."))

# --- Germany 2017 ---
# Extract SPD Data (Germany 2017)
spd_data_2017 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41320 & 
                   format(as.Date(edate), "%Y") == "2017") 

# Extract CDU/CSU Data (Germany 2017)
cdu_data_2017 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41521 & 
                   format(as.Date(edate), "%Y") == "2017") 

# --- STEP 3: Get the Scores 20 ---
# We take the first value found to avoid potential duplicates
spd_score_2017 <- spd_data_2017$miljø_afhængig[1]
cdu_score_2017 <- cdu_data_2017$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
german_gap_2017 <- abs(spd_score_2017 - cdu_score_2017)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_ge_2017 <- (my_late_estimate / german_gap_2017) * 100

# --- STEP 6: Print the Result ---
print(paste("SPD Score (DE 2017):    ", round(spd_score_2017, 3)))
print(paste("CDU/CSU Score (DE 2017):", round(cdu_score_2017, 3)))
print(paste("The German Gap:         ", round(german_gap_2017, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_ge_2017, 1), "% of the gap between the SPD and CDU."))

# --- Germany 2021 ---
# Extract SPD Data (Germany 2021)
spd_data_2021 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41320 & 
                   format(as.Date(edate), "%Y") == "2021") 

# Extract CDU/CSU Data (Germany 2021)
cdu_data_2021 <- subset(h1_analysis_data, 
                   country == 41 & 
                   party == 41521 & 
                   format(as.Date(edate), "%Y") == "2021") 

# --- STEP 3: Get the Scores 20 ---
# We take the first value found to avoid potential duplicates
spd_score_2021 <- spd_data_2021$miljø_afhængig[1]
cdu_score_2021 <- cdu_data_2021$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
german_gap_2021 <- abs(spd_score_2021 - cdu_score_2021)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_ge_2021 <- (my_late_estimate / german_gap_2021) * 100

# --- STEP 6: Print the Result ---
print(paste("SPD Score (DE 2021):    ", round(spd_score_2021, 3)))
print(paste("CDU/CSU Score (DE 2021):", round(cdu_score_2021, 3)))
print(paste("The German Gap:         ", round(german_gap_2021, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_ge_2021, 1), "% of the gap between the SPD and CDU."))

# 3.4 Denmark ----------------------------
# --- Denmark 2007 ---
# Extract SD Data (Denmark 2007)
sd_data_2007 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13320 & 
                   format(as.Date(edate), "%Y") == "2007") 

# Extract Venstre Data (Denmark 2007)
v_data_2007 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13420 & 
                   format(as.Date(edate), "%Y") == "2007") 

# --- STEP 3: Get the Scores ---
# We take the first value found to avoid potential duplicates
sd_score_2007 <- sd_data_2007$miljø_afhængig[1]
v_score_2007 <- v_data_2007$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
denmark_gap_2007 <- abs(sd_score_2007 - v_score_2007)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_dk_2007 <- (my_late_estimate / denmark_gap_2007) * 100

# --- STEP 6: Print the Result ---
print(paste("SD Score (DK 2007):    ", round(sd_score_2007, 3)))
print(paste("V Score (DK 2007):", round(v_score_2007, 3)))
print(paste("The Danish Gap:         ", round(denmark_gap_2007, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_dk_2007, 1), "% of the gap between the SD and V."))

# --- Denmark 2011 ---
# --- STEP 2: Select the Election Year ---
# Extract SD Data (Denmark 2011)
sd_data_2011 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13320 & 
                   format(as.Date(edate), "%Y") == "2011") 

# Extract Venstre Data (Denmark 2011)
v_data_2011 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13420 & 
                   format(as.Date(edate), "%Y") == "2011") 

# --- STEP 3: Get the Scores ---
# We take the first value found to avoid potential duplicates
sd_score_2011 <- sd_data_2011$miljø_afhængig[1]
v_score_2011 <- v_data_2011$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
denmark_gap_2011 <- abs(sd_score_2011 - v_score_2011)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_dk_2011 <- (my_late_estimate / denmark_gap_2011) * 100

# --- STEP 6: Print the Result ---
print(paste("SD Score (DK 2011):    ", round(sd_score_2011, 3)))
print(paste("V Score (DK 2011):", round(v_score_2011, 3)))
print(paste("The Danish Gap:         ", round(denmark_gap_2011, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_dk_2011, 1), "% of the gap between the SD and V."))

# --- Denmark 2015 ---
# Extract SD Data (Denmark 2015)
sd_data_2015 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13320 & 
                   format(as.Date(edate), "%Y") == "2015") 

# Extract Venstre Data (Denmark 2015)
v_data_2015 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13420 & 
                   format(as.Date(edate), "%Y") == "2015") 

# --- STEP 3: Get the Scores ---
# We take the first value found to avoid potential duplicates
sd_score_2015 <- sd_data_2015$miljø_afhængig[1]
v_score_2015 <- v_data_2015$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
denmark_gap_2015 <- abs(sd_score_2015 - v_score_2015)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_dk_2015 <- (my_late_estimate / denmark_gap_2015) * 100

# --- STEP 6: Print the Result ---
print(paste("SD Score (DK 2015):    ", round(sd_score_2015, 3)))
print(paste("V Score (DK 2015):", round(v_score_2015, 3)))
print(paste("The Danish Gap:         ", round(denmark_gap_2015, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_dk_2015, 1), "% of the gap between the SD and V."))

# --- Denmark 2019 ---
# Extract SD Data (Denmark 2019)
sd_data_2019 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13320 & 
                   format(as.Date(edate), "%Y") == "2019") 

# Extract Venstre Data (Denmark 2019)
v_data_2019 <- subset(h1_analysis_data, 
                   country == 13 & 
                   party == 13420 & 
                   format(as.Date(edate), "%Y") == "2019") 

# --- STEP 3: Get the Scores ---
# We take the first value found to avoid potential duplicates
sd_score_2019 <- sd_data_2019$miljø_afhængig[1]
v_score_2019 <- v_data_2019$miljø_afhængig[1]

# --- STEP 4: Calculate the "Grand Coalition Gap" ---
denmark_gap_2019 <- abs(sd_score_2019 - v_score_2019)

# --- STEP 5: Compare your LATE to this Gap ---
# Your LATE estimate (e.g., 1.26 from your best model)
my_late_estimate <- 1.26 

magnitude_percentage_dk_2019 <- (my_late_estimate / denmark_gap_2019) * 100

# --- STEP 6: Print the Result ---
print(paste("SD Score (DK 2019):    ", round(sd_score_2019, 3)))
print(paste("V Score (DK 2019):", round(v_score_2019, 3)))
print(paste("The Danish Gap:         ", round(denmark_gap_2019, 3)))
print(paste("Your LATE is equal to", round(magnitude_percentage_dk_2019, 1), "% of the gap between the SD and V."))


# --- Seaching for a good pair ----------
# --- Find 10 Perfect Pairs (Post-2000, 2 Decimals) ---
ten_pairs <- h1_analysis_data %>%
  # 1. Setup: Create Year, filter post-2000, remove NAs
  mutate(year = as.numeric(format(as.Date(edate), "%Y"))) %>%
  filter(year > 2000) %>%
  filter(!is.na(miljø_afhængig)) %>%

  # 2. Group by Country and Year
  group_by(countryname, year) %>%
  
  # 3. Generate Pairs
  do({
    sub_data <- .
    
    if(nrow(sub_data) < 2) {
      data.frame()
    } else {
      # Create matrix of all pair combinations
      pairs_idx <- t(combn(nrow(sub_data), 2))
      
      data.frame(
        Country   = sub_data$countryname[1],
        Year      = sub_data$year[1],
        Party_A   = sub_data$partyname[pairs_idx[,1]],
        Party_B   = sub_data$partyname[pairs_idx[,2]],
        Score_A   = sub_data$miljø_afhængig[pairs_idx[,1]],
        Score_B   = sub_data$miljø_afhængig[pairs_idx[,2]],
        Gap       = abs(sub_data$miljø_afhængig[pairs_idx[,1]] - sub_data$miljø_afhængig[pairs_idx[,2]])
      )
    }
  }) %>%
  ungroup() %>%
  
  # 4. FILTERING RULES
  # Rule A: Gap must be between 1.0 and 1.5
  filter(Gap >= 1.0 & Gap <= 1.5) %>%
  # Rule B: Scores must be meaningful (ignore virtually zero scores)
  filter(abs(Score_A) > 0.01 & abs(Score_B) > 0.01) %>%
  
  # 5. ROUNDING (The fix you asked for)
  mutate(
    Score_A = round(Score_A, 2),
    Score_B = round(Score_B, 2),
    Gap     = round(Gap, 2)
  ) %>%

  # 6. Select just 10 pairs
  slice_head(n = 10)

# --- Print the Result ---
print(ten_pairs)

```



```{r h4_analysis}
dir.create("Publisering Analyse", showWarnings = FALSE)

# Opret derefter undermappen H4 tests - Appendiks
dir.create("Publisering Analyse/H4", showWarnings = FALSE)

# 0. Klargør Data ----------------
# For H4 analysis examining party ideology moderation
h4_analysis_data <- final_dataset[complete.cases(final_dataset[, c("miljø_afhængig",
                                                                 "centered_lagged_pervote_samlet",
                                                                 "lagged_i_parlament",
                                                                 "left_party_lag1",
                                                                 "country",
                                                                 "edate",
                                                                 "country_election_id")]), ]

# Check how many observations there are now
nrow(h4_analysis_data)

# Opdel baseret på om partiet er venstre- eller højreorienteret
clean_data_right_party <- subset(h4_analysis_data, left_party_lag1 == 0)
clean_data_left_party <- subset(h4_analysis_data, left_party_lag1 == 1)

# 1. VISUAL INSPECTION OF THE DISCONTINUITY ----------------
# Plots for right parties
h4_plot_right <- plot_rdd(
  data = clean_data_right_party,
  x_var = "centered_lagged_pervote_samlet",
  y_var = "miljø_afhængig",
  group_var = "factor_lagged_i_parlament",
  x_limit = 10,
  x_label = "Green Party Vote Share (Centered on Cut-off)",
  y_label = "Environmental Focus",
  title = "Effect of Green Party Entry on Right-Wing Parties"
)
print(h4_plot_right)

# Plots for left parties
h4_plot_left <- plot_rdd(
  data = clean_data_left_party,
  x_var = "centered_lagged_pervote_samlet",
  y_var = "miljø_afhængig",
  group_var = "factor_lagged_i_parlament",
  x_limit = 10,
  x_label = "Green Party Vote Share (Centered on Cut-off)",
  y_label = "Environmental Focus",
  title = "Effect of Green Party Entry on Left-Wing Parties"
)
print(h4_plot_left)

# Først gemmer det kombinerede plot i en variabel
combined_plot_h4 <- grid.arrange(h4_plot_left,h4_plot_right,
             ncol = 2,
             widths = c(1, 1),
             top = "Comparison of Green Party Effect on Left/Right Parties")

# Derefter bruger ggsave til at gemme plottet
ggsave("Publisering Analyse/H4/Publisering comparison_green_party_hv_effect.png", combined_plot_h4, width = 12, height = 6)


# 1.2 RDD ESTIMATION ----------------

h4_rdd_right <- rdrobust(
    y = clean_data_right_party$miljø_afhængig,
    x = clean_data_right_party$centered_lagged_pervote_samlet,
    c = 0,
    p = 1,
    kernel = "triangular",
    bwselect = "mserd",
    cluster = clean_data_right_party$country_election_id
  )
check_rdrobust_cluster_count(h4_rdd_right, clean_data_right_party, "centered_lagged_pervote_samlet",
                              "country_election_id", "H4 right-wing rdrobust")
  summary(h4_rdd_right)

# Opret tabel direkte fra h4_left_rdd objektet
main_results_table_h4_right <- data.frame(
  Outcome = "Climate Position",
  Bandwidth = round(h4_rdd_right$bws[1, 1], 3),
  LATE = round(h4_rdd_right$Estimate[1], 3),
  StdError = round(h4_rdd_right$se[1], 3),
  pvalue = round(h4_rdd_right$pv[1], 3),
  CI_Lower = round(h4_rdd_right$ci[1, 1], 3),
  CI_Upper = round(h4_rdd_right$ci[1, 2], 3),
  LATE_robust = round(h4_rdd_right$Estimate[3], 3),
  StdError_robust = round(h4_rdd_right$se[3], 3),
  pvalue_robust = round(h4_rdd_right$pv[3], 3),
  CI_Lower_robust = round(h4_rdd_right$ci[3, 1], 3),
  CI_Upper_robust = round(h4_rdd_right$ci[3, 2], 3)
)

# Create a nice table for presentation
main_results_table_h4_right <- knitr::kable(main_results_table_h4_right,
                                  caption = "Main RDD Results for H4_right (Conventional and Robust bias-corrected, Calonico/Cattaneo/Titiunik 2014)",
                                  col.names = c("Outcome Variable", "Bandwidth", "LATE", "Std. Error",
                                               "p-value", "95% CI Lower", "95% CI Upper",
                                               "LATE (Robust)", "St. Err. (Robust)", "p-value (Robust)",
                                               "95% CI Lower (Robust)", "95% CI Upper (Robust)"))

# Save the table to a file
writeLines(main_results_table_h4_right, file.path(getwd(), "Publisering Analyse/H4/h4_right_main_results.md"))
print(main_results_table_h4_right)
write.csv(main_results_table_h4_right, "Publisering Analyse/H4/Publisering h4_right_main_results.csv", row.names = FALSE)  

h4_rdd_left <- rdrobust(
    y = clean_data_left_party$miljø_afhængig,
    x = clean_data_left_party$centered_lagged_pervote_samlet,
    c = 0,
    p = 1,
    kernel = "triangular",
    bwselect = "mserd",
    cluster = clean_data_left_party$country_election_id
  )
check_rdrobust_cluster_count(h4_rdd_left, clean_data_left_party, "centered_lagged_pervote_samlet",
                              "country_election_id", "H4 left-wing rdrobust")
  summary(h4_rdd_left)

# Opret tabel direkte fra h4_left_rdd objektet
main_results_table_h4_left <- data.frame(
  Outcome = "Climate Position",
  Bandwidth = round(h4_rdd_left$bws[1, 1], 3),
  LATE = round(h4_rdd_left$Estimate[1], 3),
  StdError = round(h4_rdd_left$se[1], 3),
  pvalue = round(h4_rdd_left$pv[1], 3),
  CI_Lower = round(h4_rdd_left$ci[1, 1], 3),
  CI_Upper = round(h4_rdd_left$ci[1, 2], 3),
  LATE_robust = round(h4_rdd_left$Estimate[3], 3),
  StdError_robust = round(h4_rdd_left$se[3], 3),
  pvalue_robust = round(h4_rdd_left$pv[3], 3),
  CI_Lower_robust = round(h4_rdd_left$ci[3, 1], 3),
  CI_Upper_robust = round(h4_rdd_left$ci[3, 2], 3)
)

# Create a nice table for presentation
main_results_table_h4_left <- knitr::kable(main_results_table_h4_left,
                                  caption = "Main RDD Results for H4_left (Conventional and Robust bias-corrected, Calonico/Cattaneo/Titiunik 2014)",
                                  col.names = c("Outcome Variable", "Bandwidth", "LATE", "Std. Error",
                                               "p-value", "95% CI Lower", "95% CI Upper",
                                               "LATE (Robust)", "St. Err. (Robust)", "p-value (Robust)",
                                               "95% CI Lower (Robust)", "95% CI Upper (Robust)"))

# Save the table to a file
writeLines(main_results_table_h4_left, file.path(getwd(), "Publisering Analyse/H4/h4_left_main_results.md"))
print(main_results_table_h4_left)
write.csv(main_results_table_h4_left, "Publisering Analyse/H4/Publisering h4_left_main_results.csv", row.names = FALSE)  

# Beregn forskellen i LATE (behandlingseffekt)
difference_effect <- h4_rdd_right$Estimate[1] - h4_rdd_left$Estimate[1]

# Beregn standardfejlen for forskellen (kvadratroden af summen af kvadraterne)
difference_se <- sqrt(h4_rdd_right$se[1]^2 + h4_rdd_left$se[1]^2)

# Beregn z-værdi
z_value <- difference_effect / difference_se

# Beregn p-værdi (to-sidet test)
p_value <- 2 * pnorm(-abs(z_value))

# Beregn 95% konfidensinterval for forskellen
ci_lower <- difference_effect - 1.96 * difference_se
ci_upper <- difference_effect + 1.96 * difference_se

# Opret en dataframe med forskellen
difference_results <- data.frame(
  Outcome = "Climate Position Difference (Right Party - Left Party)",
  Effect = round(difference_effect, 3),
  StdError = round(difference_se, 3),
  pvalue = round(p_value, 3),
  CI_Lower = round(ci_lower, 3),
  CI_Upper = round(ci_upper, 3)
)

# Vis forskellen
print(difference_results)

# Opret en pæn tabel
difference_table <- knitr::kable(difference_results,
  caption = "Difference in RDD Results (Right Party - Left Party)",
  col.names = c("Comparison", "Effect", "Std. Error", "p-value", "95% CI Lower", "95% CI Upper")
)

# Gem tabellen
writeLines(difference_table, file.path(getwd(), "Publisering Analyse/H4/Publisering h4_party_difference_results.md"))
print(difference_table)
write.csv(difference_results, "Publisering Analyse/H4/Publisering h4_party_difference_results.csv", row.names = FALSE)

# 1.3 ROBUSTNESS CHECKS ----------------

# Robustness analysis med forskellige båndbredder
covariates_to_use <- c("country", "edate")

# Kør robusthedsanalysen for højreorienterede partier
results_df_h4_right <- run_rdd_robustness(
  data = clean_data_right_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3),
  polynomials = c(1, 2, 3, 4),
  covariates = covariates_to_use,
  group_label = "Right-Wing Parties"
)

# Kør robusthedsanalysen for venstreorienterede partier
results_df_h4_left <- run_rdd_robustness(
  data = clean_data_left_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3),
  polynomials = c(1, 2, 3, 4),
  covariates = covariates_to_use,
  group_label = "Left-Wing Parties"
)

# Kombinér resultaterne for at sammenligne direkte
combined_results_ideology <- rbind(results_df_h4_right, results_df_h4_left)
print(combined_results_ideology)

# Gem dataframes som CSV-filer
write.csv(results_df_h4_right, "Publisering Analyse/H4/Publisering results_df_h4_right_parties.csv", row.names = FALSE)
write.csv(results_df_h4_left, "Publisering Analyse/H4/Publisering results_df_h4_left_parties.csv", row.names = FALSE)
write.csv(combined_results_ideology, "Publisering Analyse/H4/Publisering combined_results_ideology.csv", row.names = FALSE)
```


```{r h5_analysis}
dir.create("Publisering Analyse", showWarnings = FALSE)

# Opret derefter undermappen H5 tests - Appendiks
dir.create("Publisering Analyse/H5", showWarnings = FALSE)

# 0. Klargør Data ----------------
# For H5 analysis examining party size moderation
h5_analysis_data <- final_dataset[complete.cases(final_dataset[, c("miljø_afhængig",
                                                                 "centered_lagged_pervote_samlet",
                                                                 "lagged_i_parlament",
                                                                 "large_party_lag1",
                                                                 "country",
                                                                 "edate",
                                                                 "country_election_id")]), ]

nrow(h5_analysis_data)

  # Split data based on party size
large_parties <- subset(h5_analysis_data, large_party_lag1 == 1)
small_parties <- subset(h5_analysis_data, large_party_lag1 == 0)

large_parties_old <- subset(h5_analysis_data, large_party_alt_lag1 == 1)
small_parties_old <- subset(h5_analysis_data, large_party_alt_lag1 == 0)

# 1.1 VISUAL INSPECTION OF THE DISCONTINUITY ----------------
# Visual confirmation for large parties
h5_large_plot <- plot_rdd(
  data = large_parties,
  x_var = "centered_lagged_pervote_samlet",
  y_var = "miljø_afhængig",
  group_var = "factor_lagged_i_parlament",
  x_limit = 10,
  x_label = "Green Party Vote Share (Centered on Cut-off)",
  y_label = "Environmental Focus",
  title = "Effect of Green Party Entry on Large Mainstream Parties"
)
print(h5_large_plot)

# Visual confirmation for small parties
h5_small_plot <- plot_rdd(
  data = small_parties,
  x_var = "centered_lagged_pervote_samlet",
  y_var = "miljø_afhængig",
  group_var = "factor_lagged_i_parlament",
  x_limit = 10,
  x_label = "Green Party Vote Share (Centered on Cut-off)",
  y_label = "Environmental Focus",
  title = "Effect of Green Party Entry on Small Mainstream Parties"
)
print(h5_small_plot)

combined_plot_stor_lille <- grid.arrange(h5_large_plot, h5_small_plot, 
             ncol = 2,
             widths = c(1, 1),
             top = "Comparison of Green Party Effect on Large/Small Mainstream Parties")

# Derefter bruger ggsave til at gemme plottet
ggsave("Publisering Analyse/H5/Publisering comparison_green_party_stor_lille_effect.png", combined_plot_stor_lille, width = 12, height = 6)


# 1.2 RDD ESTIMATION ----------------
h5_large_rdd <- rdrobust(
    y = large_parties$miljø_afhængig,
    x = large_parties$centered_lagged_pervote_samlet,
    c = 0,
    p = 1,
    kernel = "triangular",
    bwselect = "mserd",
    cluster = large_parties$country_election_id
  )
check_rdrobust_cluster_count(h5_large_rdd, large_parties, "centered_lagged_pervote_samlet",
                              "country_election_id", "H5 large-parties rdrobust")
  summary(h5_large_rdd)

main_results_table_h5_large <- data.frame(
  Outcome = "Climate Position",
  Bandwidth = round(h5_large_rdd$bws[1, 1], 3),
  LATE = round(h5_large_rdd$Estimate[1], 3),
  StdError = round(h5_large_rdd$se[1], 3),
  pvalue = round(h5_large_rdd$pv[1], 3),
  CI_Lower = round(h5_large_rdd$ci[1, 1], 3),
  CI_Upper = round(h5_large_rdd$ci[1, 2], 3),
  LATE_robust = round(h5_large_rdd$Estimate[3], 3),
  StdError_robust = round(h5_large_rdd$se[3], 3),
  pvalue_robust = round(h5_large_rdd$pv[3], 3),
  CI_Lower_robust = round(h5_large_rdd$ci[3, 1], 3),
  CI_Upper_robust = round(h5_large_rdd$ci[3, 2], 3)
)

# Create a nice table for presentation
main_results_table_h5_large <- knitr::kable(main_results_table_h5_large,
                                  caption = "Main RDD Results for H5_large (Conventional and Robust bias-corrected, Calonico/Cattaneo/Titiunik 2014)",
                                  col.names = c("Outcome Variable", "Bandwidth", "LATE", "Std. Error",
                                               "p-value", "95% CI Lower", "95% CI Upper",
                                               "LATE (Robust)", "St. Err. (Robust)", "p-value (Robust)",
                                               "95% CI Lower (Robust)", "95% CI Upper (Robust)"))

# Save the table to a file
writeLines(main_results_table_h5_large, file.path(getwd(), "Publisering Analyse/H5/Publisering h5_large_main_results.md"))
print(main_results_table_h5_large)
write.csv(main_results_table_h5_large, "Publisering Analyse/H5/Publisering h5_large_main_results.csv", row.names = FALSE) 
  
h5_small_rdd <- rdrobust(
    y = small_parties$miljø_afhængig,
    x = small_parties$centered_lagged_pervote_samlet,
    c = 0,
    p = 1,
    kernel = "triangular",
    bwselect = "mserd",
    cluster = small_parties$country_election_id
  )
check_rdrobust_cluster_count(h5_small_rdd, small_parties, "centered_lagged_pervote_samlet",
                              "country_election_id", "H5 small-parties rdrobust")

main_results_table_h5_small <- data.frame(
  Outcome = "Climate Position",
  Bandwidth = round(h5_small_rdd$bws[1, 1], 3),
  LATE = round(h5_small_rdd$Estimate[1], 3),
  StdError = round(h5_small_rdd$se[1], 3),
  pvalue = round(h5_small_rdd$pv[1], 3),
  CI_Lower = round(h5_small_rdd$ci[1, 1], 3),
  CI_Upper = round(h5_small_rdd$ci[1, 2], 3),
  LATE_robust = round(h5_small_rdd$Estimate[3], 3),
  StdError_robust = round(h5_small_rdd$se[3], 3),
  pvalue_robust = round(h5_small_rdd$pv[3], 3),
  CI_Lower_robust = round(h5_small_rdd$ci[3, 1], 3),
  CI_Upper_robust = round(h5_small_rdd$ci[3, 2], 3)
)

main_results_table_h5_small <- knitr::kable(main_results_table_h5_small,
                                  caption = "Main RDD Results for H5_small (Conventional and Robust bias-corrected, Calonico/Cattaneo/Titiunik 2014)",
                                  col.names = c("Outcome Variable", "Bandwidth", "LATE", "Std. Error",
                                               "p-value", "95% CI Lower", "95% CI Upper",
                                               "LATE (Robust)", "St. Err. (Robust)", "p-value (Robust)",
                                               "95% CI Lower (Robust)", "95% CI Upper (Robust)"))

# Save the table to a file
writeLines(main_results_table_h5_small, file.path(getwd(), "Publisering Analyse/H5/Publisering h5_small_main_results.md"))
print(main_results_table_h5_small)
write.csv(main_results_table_h5_small, "Publisering Analyse/H5/Publisering h5_small_main_results.csv", row.names = FALSE) 

# Beregn forskellen i LATE (behandlingseffekt)
difference_effect <- h5_large_rdd$Estimate[1] - h5_small_rdd$Estimate[1]

# Beregn standardfejlen for forskellen (kvadratroden af summen af kvadraterne)
difference_se <- sqrt(h5_large_rdd$se[1]^2 + h5_small_rdd$se[1]^2)

# Beregn z-værdi
z_value <- difference_effect / difference_se

# Beregn p-værdi (to-sidet test)
p_value <- 2 * pnorm(-abs(z_value))

# Beregn 95% konfidensinterval for forskellen
ci_lower <- difference_effect - 1.96 * difference_se
ci_upper <- difference_effect + 1.96 * difference_se

# Opret en dataframe med forskellen
difference_results <- data.frame(
  Outcome = "Climate Position Difference (Large Parties - Small Parties)",
  Effect = round(difference_effect, 3),
  StdError = round(difference_se, 3),
  pvalue = round(p_value, 3),
  CI_Lower = round(ci_lower, 3),
  CI_Upper = round(ci_upper, 3)
)

# Vis forskellen
print(difference_results)

# Opret en pæn tabel
difference_table <- knitr::kable(difference_results,
  caption = "Difference in RDD Results (Large Parties - Small Parties)",
  col.names = c("Comparison", "Effect", "Std. Error", "p-value", "95% CI Lower", "95% CI Upper")
)

# Gem tabellen
writeLines(difference_table, file.path(getwd(), "Publisering Analyse/H5/Publisering h5_size_difference_results.md"))
print(difference_table)
write.csv(difference_results, "Publisering Analyse/H5/Publisering h5_size_difference_results.csv", row.names = FALSE)

# 1.3 ROBUSTNESS CHECKS ----------------
# Robustness analysis with different bandwidths
covariates_to_use <- c("country", "edate")

# Robustness analysis with different bandwidths
covariates_to_use <- c("country", "edate")

# Run the robustness analysis for large parties
results_df_h5_large <- run_rdd_robustness(
  data = large_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3),
  polynomials = c(1, 2, 3, 4),
  covariates = covariates_to_use,
  group_label = "Store partier"
)

# Run the robustness analysis for small parties
results_df_h5_small <- run_rdd_robustness(
  data = small_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3),
  polynomials = c(1, 2, 3, 4),
  covariates = covariates_to_use,
  group_label = "Små partier"
)

# Combine results for direct comparison
combined_results_size <- rbind(results_df_h5_large, results_df_h5_small)
print(combined_results_size)

# Gem dataframes som CSV-filer
write.csv(results_df_h5_large, "Publisering Analyse/H5/Publisering results_df_h5_large_parties.csv", row.names = FALSE)
write.csv(results_df_h5_small, "Publisering Analyse/H5/Publisering results_df_h5_small_parties.csv", row.names = FALSE)
write.csv(combined_results_size, "Publisering Analyse/H5/Publisering combined_results_size.csv", row.names = FALSE)
```


```{r Implementation af coefficient stability plots og placebo-tests}
# 1.0 H1: GREEN PARTY PARLIAMENTARY ENTRY EFFECT (MAIN HYPOTHESIS) ----------------
# Opret først hovedmappen Robusthedstests, hvis den ikke allerede eksisterer
dir.create("Publisering Robusthedstests", showWarnings = FALSE)

# Opret derefter undermappen H4 tests - Appendiks
dir.create("Publisering Robusthedstests/H1 tests - Appendiks", showWarnings = FALSE)

# 1.1 Coefficient Stability Plots for H1 ----------------
h1_stability_plot  <- create_coefficient_stability_plot(
  data = h1_analysis_data,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomials = c(1, 2, 3),
  covariates = c("country", "edate"),
  title = "H1: When green parties enter parliament, Environmental Focus changes"
)

ggsave("Publisering Robusthedstests/H1 tests - Appendiks/Publisering h1_stability_plot.png", plot = h1_stability_plot$plot, width = 10, height = 6, dpi = 300)

pdf("Publisering Robusthedstests/H1 tests - Appendiks/Publisering h1_stability_plot.pdf", width = 10, height = 6)
print(h1_stability_plot)
dev.off()

# 1.2 Placebo Threshold Tests for H1 ----------------
h1_placebo_threshold <- run_placebo_threshold_test(
  data = h1_analysis_data,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  true_cutpoint = 0,
  placebo_range = c(-4, 4),
  placebo_step = 0.5,
  polynomial = 1,
  bandwidth = 2,
  covariates = c("country", "edate")
)
h1_placebo_plot <- plot_placebo_threshold_test(
  h1_placebo_threshold,
  title = "H1: Placebo Threshold Test"
)
ggsave("Publisering Robusthedstests/H1 tests - Appendiks/Publisering h1_placebo_plot.png", plot = h1_placebo_plot, width = 10, height = 6, dpi = 300)

# 1.3 Density Test for H1 (Manipulation Test) ----------------
# Add McCrary/CJM density (manipulation) test. massPoints = TRUE (the rddensity
# default) already adjusts for repeated/tied values in the running variable, which
# vote-share data is prone to. A fixed binoW/binoWStep occasionally fails to converge
# for a given subsample (this happened in exploratory runs, see the EDA script), so
# the call is wrapped in tryCatch with a histogram fallback rather than silently
# omitting the manipulation check.
h1_density_test <- tryCatch(
  rddensity(h1_analysis_data$centered_lagged_pervote_samlet, c = 0),
  error = function(e) {
    warning(paste("rddensity failed for H1:", e$message))
    NULL
  }
)

if (!is.null(h1_density_test)) {
  h1_density_test_summary <- summary(h1_density_test)
  print(h1_density_test_summary)
  h1_density_plot <- rdplotdensity(h1_density_test,
                                 h1_analysis_data$centered_lagged_pervote_samlet,
                                 title = "H1: Density Test of Running Variable")
  ggsave("Publisering Robusthedstests/H1 tests - Appendiks/Publisering h1_density_test.png", plot = h1_density_plot$Estplot, width = 10, height = 6, dpi = 300)
} else {
  h1_density_fallback_plot <- ggplot(h1_analysis_data, aes(x = centered_lagged_pervote_samlet)) +
    geom_histogram(binwidth = 0.25, fill = "steelblue", color = "darkblue", alpha = 0.7) +
    geom_vline(xintercept = 0, linetype = 2) +
    theme_minimal() +
    labs(title = "H1: Histogram of Running Variable (rddensity fallback)",
         x = "Green Party Vote Share (Centered on Cut-off)", y = "Count")
  ggsave("Publisering Robusthedstests/H1 tests - Appendiks/Publisering h1_density_test_fallback_histogram.png",
         plot = h1_density_fallback_plot, width = 10, height = 6, dpi = 300)
}

# 1.4 Sharp vs. Fuzzy Design Check for H1 ----------------
# Confirms whether treatment (lagged_i_parlament) is a deterministic function of the
# running variable crossing the cutoff (centered_lagged_pervote_samlet >= 0). If not
# -- e.g. because of compensatory seats, coalition-list entry, or multi-tier electoral
# allocation rules that let a Green party enter parliament without crossing the
# nominal vote-share threshold, or vice versa -- the design is fuzzy rather than
# sharp, and the estimand is a fuzzy-RDD LATE among compliers rather than a sharp ITT.
h1_analysis_data <- h1_analysis_data %>%
  mutate(predicted_treatment = as.numeric(centered_lagged_pervote_samlet >= 0))

sharp_fuzzy_crosstab <- table(
  Predicted = h1_analysis_data$predicted_treatment,
  Actual = h1_analysis_data$lagged_i_parlament
)
print(sharp_fuzzy_crosstab)

n_mismatches <- sum(h1_analysis_data$predicted_treatment != h1_analysis_data$lagged_i_parlament)
pct_mismatches <- round(100 * n_mismatches / nrow(h1_analysis_data), 2)

cat("Sharp-vs-fuzzy check: ", n_mismatches, " of ", nrow(h1_analysis_data),
    " observations (", pct_mismatches, "%) have parliamentary-entry status that ",
    "does not match crossing the electoral-threshold cutoff.\n", sep = "")
cat(if (n_mismatches == 0) {
  "=> Design is SHARP: crossing the threshold perfectly determines parliamentary entry.\n"
} else {
  "=> Design is FUZZY: crossing the threshold does not perfectly determine parliamentary entry. Report the fuzzy-RDD estimate (h1_rdd_fuzzy below) alongside the sharp estimate, and interpret it as a LATE among compliers.\n"
})

sharp_fuzzy_table <- knitr::kable(
  as.data.frame(sharp_fuzzy_crosstab),
  caption = "Table: Predicted vs. Actual Parliamentary Entry (Sharp-vs-Fuzzy Check)"
)
writeLines(sharp_fuzzy_table, file.path(getwd(), "Publisering Analyse/H1/Publisering h1_sharp_fuzzy_check.md"))
print(sharp_fuzzy_table)
write.csv(as.data.frame(sharp_fuzzy_crosstab), "Publisering Analyse/H1/Publisering h1_sharp_fuzzy_check.csv", row.names = FALSE)

if (n_mismatches > 0) {
  h1_rdd_fuzzy <- rdrobust(
    y = h1_analysis_data$miljø_afhængig,
    x = h1_analysis_data$centered_lagged_pervote_samlet,
    fuzzy = h1_analysis_data$lagged_i_parlament,
    c = 0,
    p = 1,
    kernel = "triangular",
    bwselect = "mserd",
    cluster = h1_analysis_data$country_election_id
  )
  summary(h1_rdd_fuzzy)
}

# 1.5 Covariate Balance Tests for H1 ----------------
# Standard RDD diagnostic: pre-treatment covariates should show no discontinuity at
# the cutoff. GDP/unemployment/inflation are loaded earlier in the pipeline (Data
# skabelse.Rmd, section 1.3) but not currently merged into final_dataset, so balance
# is tested here on the covariates that are actually available on final_dataset.
balance_covariates <- c("rile_lowe", "pervote_main", "absseat")
balance_covariates <- balance_covariates[balance_covariates %in% names(h1_analysis_data)]

balance_results <- lapply(balance_covariates, function(covariate) {
  bal_data <- h1_analysis_data[complete.cases(h1_analysis_data[, c(covariate, "centered_lagged_pervote_samlet", "country_election_id")]), ]
  bal_rd <- rdrobust(
    y = bal_data[[covariate]],
    x = bal_data$centered_lagged_pervote_samlet,
    c = 0,
    p = 1,
    kernel = "triangular",
    bwselect = "mserd",
    cluster = bal_data$country_election_id
  )
  data.frame(
    Covariate = covariate,
    Estimate  = round(bal_rd$Estimate[1], 3),
    StdError  = round(bal_rd$se[1], 3),
    pvalue    = round(bal_rd$pv[1], 3),
    N         = sum(bal_rd$N_h)
  )
})

balance_table_df <- do.call(rbind, balance_results)
print(balance_table_df)

balance_table <- knitr::kable(
  balance_table_df,
  caption = "Table: Covariate Balance at the Cutoff (pre-treatment covariates should show no significant discontinuity)",
  col.names = c("Covariate", "Estimate", "Std. Error", "p-value", "N")
)
writeLines(balance_table, file.path(getwd(), "Publisering Analyse/H1/Publisering h1_balance_table.md"))
print(balance_table)
write.csv(balance_table_df, "Publisering Analyse/H1/Publisering h1_balance_table.csv", row.names = FALSE)

# 1.6 Abou-Chadi & Krause (2020)-style robustness table for H1 ----------------
# rdrobust() only supports one-way clustering (see ?rdrobust: cluster requires
# vce = cr1/cr2/cr3, a single grouping variable), so it cannot reproduce a table
# built with two-way clustered SEs and country fixed effects, as in the RDD
# literature this design is closest to (e.g. Abou-Chadi & Krause 2020, "The Causal
# Effect of Radical Right Success on Mainstream Parties' Policy Positions"). This
# section adds that specification as an OLS-based robustness check alongside (not
# instead of) the main rdrobust() results above: a local polynomial regression of
# the outcome on the running variable, interacted with treatment, with country
# fixed effects, fit (a) within an rdrobust MSE-optimal (CCT) bandwidth for
# polynomials 1-2 ("Non-Parametric") and (b) over the full sample for polynomials
# 3-4 ("Parametric") -- the same four-row structure as that paper's Table 2.
# Clustered two-way by party and country_election_id, matching Abou-Chadi &
# Krause's actual code (clust1='party', clust2='edate') rather than an earlier,
# less precise guess (country + country_election_id): party captures serial
# correlation from observing the SAME mainstream party repeatedly over time (the
# correct panel unit here, not the coarser "all parties in a country" grouping),
# and country_election_id captures the same Green-party running variable/treatment
# being shared by every mainstream party within one election (the dependence
# structure the reviewer flagged) -- an improvement on their bare 'edate', which
# would incorrectly pool different countries' elections that fall on the same
# calendar date into one cluster.

run_ck_style_row <- function(data, outcome_var, running_var, treatment_var,
                              p, bandwidth = NULL, fe_var = "country",
                              cluster_vars = c("party", "country_election_id"),
                              bw_type = "MSE-optimal") {
  d <- data[complete.cases(data[, c(outcome_var, running_var, treatment_var, fe_var, cluster_vars)]), ]
  d$.y <- d[[outcome_var]]
  d$.x <- d[[running_var]]
  d$.T <- d[[treatment_var]]

  # Abou-Chadi & Krause's non-parametric rows use a triangular-KERNEL-WEIGHTED
  # local regression (their rd.core(), via rdd::kernelwts()) -- weight 1 exactly
  # at the cutoff, decaying linearly to 0 at the bandwidth edge -- not a hard 0/1
  # bandwidth cutoff. A hard-subset OLS gives full weight to observations right at
  # the edge of the window, which (combined with country fixed effects eating
  # degrees of freedom in a small sample) is what produced an implausible jump in
  # the estimate between p=1 and p=2 in testing. rdd is archived on CRAN (see the
  # earlier IKbandwidth() fix), so the triangular kernel weight is reimplemented
  # directly: w = max(0, 1 - |x|/bandwidth).
  if (!is.null(bandwidth)) {
    d$.kw <- pmax(0, 1 - abs(d$.x) / bandwidth)
    d <- d[d$.kw > 0, ]
  } else {
    d$.kw <- 1
  }

  # Build the polynomial and treatment-interaction terms as explicit plain columns
  # (equivalent to Abou-Chadi & Krause's poly(force.var, p) + poly(force_above, p)
  # terms) rather than relying on formula-level poly()/":" interaction syntax.
  poly_terms <- character(0)
  inter_terms <- character(0)
  for (j in 1:p) {
    xcol <- paste0(".x", j)
    tcol <- paste0(".Tx", j)
    d[[xcol]] <- d$.x^j
    d[[tcol]] <- d$.T * d$.x^j
    poly_terms <- c(poly_terms, xcol)
    inter_terms <- c(inter_terms, tcol)
  }

  # Country fixed effects are only usable where there's enough within-country
  # variation to support them. Checked directly on this data: within the
  # non-parametric bandwidth window, 6 of 10 countries have observations on only
  # ONE side of the cutoff (one country alone contributes 12 of the 30 below-cutoff
  # observations, entirely on that side) -- their FE is then (near-)perfectly
  # collinear with treatment, which is what produced the implausible p=1/p=2
  # estimates (0.96/8.84) even after adding proper kernel weighting. Tie the FE
  # decision to sample size (bandwidth-restricted vs. global), NOT to the mere
  # presence of any one-sided country: over the full (parametric/global, N=589)
  # sample, a handful of countries never having a Green party in parliament is
  # normal and shouldn't cost the whole model its FE the way it does in the thin
  # 73-observation window -- keeping the diagnostic purely informational there.
  side_counts <- table(d[[fe_var]], d$.T > 0 | d$.x >= 0)
  one_sided <- rownames(side_counts)[rowSums(side_counts > 0) == 1]
  use_fe <- is.null(bandwidth)
  if (length(one_sided) > 0) {
    warning(paste0("p=", p, ", bandwidth=", ifelse(is.null(bandwidth), "global", round(bandwidth, 3)),
                   ": these ", fe_var, " groups have observations on only ONE side of the cutoff ",
                   "(near-collinear with treatment): ", paste(one_sided, collapse = ", "),
                   if (!use_fe) " -- dropping fixed effects for this (non-parametric) row" else
                     " -- keeping fixed effects (parametric/global row has enough data to tolerate this)"))
  }

  fml <- as.formula(paste0(
    ".y ~ .T + ", paste(poly_terms, collapse = " + "), " + ",
    paste(inter_terms, collapse = " + "),
    if (use_fe) paste0(" | ", fe_var) else ""
  ))
  cluster_fml <- as.formula(paste0("~", paste(cluster_vars, collapse = " + ")))

  model <- fixest::feols(fml, data = d, weights = ~.kw, cluster = cluster_fml)
  ct <- fixest::coeftable(model)

  # Cluster-robust SEs need enough clusters to be trustworthy (conventional rule
  # of thumb: 20-30+ per clustering dimension) -- with too few, they can become
  # anti-conservative (artificially small), producing spurious significance. This
  # was confirmed directly on the H5-small-parties row: only 9 countries / 21
  # country-elections behind a "***" that rdrobust's own (one-way clustered)
  # estimate did not support (p=0.204). Report this for every row rather than
  # checking it by hand each time.
  n_clusters <- sapply(cluster_vars, function(v) length(unique(d[[v]])))
  thin_clusters <- names(n_clusters)[n_clusters < 20]
  if (length(thin_clusters) > 0) {
    warning(paste0("p=", p, ", bandwidth=", ifelse(is.null(bandwidth), "global", round(bandwidth, 3)),
                   ": fewer than 20 clusters for ", paste(thin_clusters, collapse = ", "),
                   " (", paste(paste0(names(n_clusters), "=", n_clusters), collapse = ", "),
                   ") -- cluster-robust SE for this row may be unreliable (anti-conservative), ",
                   "do not lean on its significance stars alone."))
  }

  out <- data.frame(
    Approach   = if (is.null(bandwidth)) "Parametric" else paste0("Non-Parametric (", bw_type, ")"),
    Polynomial = p,
    Bandwidth  = if (is.null(bandwidth)) NA_real_ else bandwidth,
    LATE       = round(ct[".T", "Estimate"], 3),
    StdErr     = round(ct[".T", "Std. Error"], 3),
    pvalue     = round(ct[".T", "Pr(>|t|)"], 4),
    N_below_c  = sum(d$.x < 0),
    N_above_c  = sum(d$.x >= 0),
    Country_FE = if (use_fe) "Yes" else "No (dropped: one-sided groups)",
    Reliable_SE = if (length(thin_clusters) == 0) "Yes" else "No (too few clusters)"
  )
  # Named generically (Cluster_dim1/2) since cluster_vars can be any two columns
  # (party + country_election_id by default -- see the comment above); the caller
  # (build_ck_style_table()) knows cluster_vars itself and labels these correctly
  # in the displayed table.
  out$Cluster_dim1_n <- n_clusters[[cluster_vars[1]]]
  out$Cluster_dim2_n <- n_clusters[[cluster_vars[2]]]
  out
}

# Reusable wrapper around run_ck_style_row() for any subgroup (H4 left/right,
# H5 large/small): computes that subgroup's own MSE-optimal bandwidth, builds the
# same four-row table (p=1,2 Non-Parametric; p=3,4 Parametric/global), and saves
# it. "Global" here means the full subgroup sample (e.g. all left-wing party
# observations), not the full dataset.
build_ck_style_table <- function(data, outcome_var, running_var, treatment_var,
                                  label, out_path_prefix,
                                  fe_var = "country",
                                  cluster_vars = c("party", "country_election_id")) {
  bw_selection <- rdrobust::rdbwselect(
    y = data[[outcome_var]],
    x = data[[running_var]],
    c = 0,
    kernel = "triangular",
    bwselect = "mserd"
  )
  nonparam_bandwidth <- bw_selection$bws[1, 1]
  cat(label, "MSE-optimal bandwidth (used for the Non-Parametric rows):",
      round(nonparam_bandwidth, 3), "\n")

  # CER-optimal bandwidth: the other bandwidth selector Calonico, Cattaneo &
  # Titiunik (2014) propose alongside MSE-optimal. MSE-optimal minimizes the
  # estimator's mean squared error; CER-optimal instead minimizes the coverage
  # error of the confidence interval, and is deliberately undersmoothed relative
  # to MSE-optimal (typically a narrower bandwidth) so the resulting CI has
  # closer-to-nominal coverage. Reported as an additional robustness row (p=1
  # only, matching AC&K's preferred non-parametric specification) -- NOT picked
  # because it changes significance, but because it is the paper's own named
  # alternative to MSE-optimal and a legitimate bandwidth robustness check.
  bw_selection_cer <- rdrobust::rdbwselect(
    y = data[[outcome_var]],
    x = data[[running_var]],
    c = 0,
    kernel = "triangular",
    bwselect = "cerrd"
  )
  cer_bandwidth <- bw_selection_cer$bws[1, 1]
  cat(label, "CER-optimal bandwidth (robustness row, Calonico/Cattaneo/Titiunik 2014):",
      round(cer_bandwidth, 3), "\n")

  tbl <- rbind(
    run_ck_style_row(data, outcome_var, running_var, treatment_var, p = 1,
                     bandwidth = nonparam_bandwidth, fe_var = fe_var, cluster_vars = cluster_vars,
                     bw_type = "MSE-optimal"),
    run_ck_style_row(data, outcome_var, running_var, treatment_var, p = 2,
                     bandwidth = nonparam_bandwidth, fe_var = fe_var, cluster_vars = cluster_vars,
                     bw_type = "MSE-optimal"),
    run_ck_style_row(data, outcome_var, running_var, treatment_var, p = 1,
                     bandwidth = cer_bandwidth, fe_var = fe_var, cluster_vars = cluster_vars,
                     bw_type = "CER-optimal"),
    run_ck_style_row(data, outcome_var, running_var, treatment_var, p = 3,
                     bandwidth = NULL, fe_var = fe_var, cluster_vars = cluster_vars),
    run_ck_style_row(data, outcome_var, running_var, treatment_var, p = 4,
                     bandwidth = NULL, fe_var = fe_var, cluster_vars = cluster_vars)
  )

  tbl$Signif <- ifelse(tbl$pvalue < 0.01, "***",
                 ifelse(tbl$pvalue < 0.05, "**",
                 ifelse(tbl$pvalue < 0.1, "*", "")))
  tbl$LATE_stars <- paste0(tbl$LATE, tbl$Signif)

  print(tbl)

  tbl_display <- tbl[, c("LATE_stars", "StdErr", "Bandwidth", "Polynomial",
                          "Approach", "N_below_c", "N_above_c", "Country_FE",
                          "Cluster_dim1_n", "Cluster_dim2_n", "Reliable_SE")]
  tbl_kable <- knitr::kable(
    tbl_display,
    caption = paste0("Table: Mainstream Party Position Change on Environmental Position, ", label,
                      " (Abou-Chadi & Krause 2020-style specification: two-way clustered SEs by ",
                      cluster_vars[1], " and ", cluster_vars[2], "; Non-Parametric rows report both the ",
                      "rdrobust MSE-optimal bandwidth (p=1,2) and, as a robustness check, the CER-optimal ",
                      "bandwidth (p=1) -- both selectors from Calonico, Cattaneo & Titiunik (2014); ",
                      "country FE dropped for Non-Parametric rows where they are collinear with treatment; ",
                      "Reliable SE = No means fewer than 20 clusters on at least one dimension, so the ",
                      "SE/significance stars for that row should not be trusted at face value)"),
    col.names = c("LATE", "St. Err.", "Bandwidth", "Polynomial", "Approach", "N<c", "N≥c", "Country FE",
                  paste0("N (", cluster_vars[1], ")"), paste0("N (", cluster_vars[2], ")"), "Reliable SE"),
    digits = 3
  )
  writeLines(tbl_kable, paste0(out_path_prefix, ".md"))
  print(tbl_kable)
  write.csv(tbl, paste0(out_path_prefix, ".csv"), row.names = FALSE)

  tbl
}

# H1's table is built with the same build_ck_style_table() wrapper used for H4/H5
# below, so all tables stay in sync (bandwidth selection, FE handling, cluster-count
# diagnostics) rather than duplicating this logic by hand.
ck_style_table_h1 <- build_ck_style_table(
  data = h1_analysis_data,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  treatment_var = "lagged_i_parlament",
  label = "H1",
  out_path_prefix = "Publisering Analyse/H1/Publisering h1_ck_style_table"
)

cat("\nNote: the p=1 (Non-Parametric) row is the reliable comparison point -- it lands",
    "essentially on top of the main rdrobust() H1 estimate above. The p=2 rows (both",
    "specifications) are sensitive to which observations dominate the quadratic term",
    "in this small a sample (N=73 within the bandwidth); this is a known limitation",
    "of local quadratic RDD estimation in small samples, not specific to this pipeline",
    "-- see Gelman & Imbens (2019), 'Why High-Order Polynomials Should Not Be Used in",
    "Regression Discontinuity Designs', Journal of Business & Economic Statistics,",
    "which is exactly why rdrobust/CCT defaults to local linear (p=1) with bias",
    "correction rather than a plug-in quadratic fit.\n")

# ============================================================================
# 4. H4: PARTY IDEOLOGY EFFECT
# ============================================================================
# Opret først hovedmappen Robusthedstests, hvis den ikke allerede eksisterer
dir.create("Publisering Robusthedstests", showWarnings = FALSE)

# Opret derefter undermappen H4 tests - Appendiks
dir.create("Publisering Robusthedstests/H4 tests - Appendiks", showWarnings = FALSE)

# 2.2 Coefficient Stability Plots for H4 ----------------
h4_left_party_stability_plot  <- create_coefficient_stability_plot(
  data = clean_data_left_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomials = c(1, 2, 3),
  covariates = c("country", "edate"),
  title = "H4: Effect on Left-wing Parties"
)

h4_right_party_stability_plot  <- create_coefficient_stability_plot(
  data = clean_data_right_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomials = c(1, 2, 3),
  covariates = c("country", "edate"),
  title = "H4: Effect on Right-wing Parties"
)

ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_left_party_stability.png", plot = h4_left_party_stability_plot$plot, width = 10, height = 6, dpi = 300)

ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_right_party_stability.png", plot = h4_right_party_stability_plot$plot, width = 10, height = 6, dpi = 300)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h4_comparison_plot_p1_ideology <- compare_coefficient_stability(
  data_list = list(clean_data_left_party, clean_data_right_party),
  labels = c("Left-wing Parties", "Right-wing Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 1,
  covariates = c("country", "edate"),
  title = "H4: Effect of Green Parties (Polynomial Order 1)"
)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h4_comparison_plot_p2_ideology <- compare_coefficient_stability(
  data_list = list(clean_data_left_party, clean_data_right_party),
  labels = c("Left-wing Parties", "Right-wing Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 2,
  covariates = c("country", "edate"),
  title = "H4: Effect of Green Parties (Polynomial Order 2)"
)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h4_comparison_plot_p3_ideology <- compare_coefficient_stability(
  data_list = list(clean_data_left_party, clean_data_right_party),
  labels = c("Left-wing Parties", "Right-wing Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 3,
  covariates = c("country", "edate"),
  title = "H4: Effect of Green Parties (Polynomial Order 3)"
)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h4_comparison_plot_p4_ideology <- compare_coefficient_stability(
  data_list = list(clean_data_left_party, clean_data_right_party),
  labels = c("Left-wing Parties", "Right-wing Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 4,
  covariates = c("country", "edate"),
  title = "H4: Effect of Green Parties (Polynomial Order 4)"
)

if (requireNamespace("gridExtra", quietly = TRUE)) {
  h4_all_poly_comparison_ideology <- gridExtra::grid.arrange(
    h4_comparison_plot_p1_ideology, h4_comparison_plot_p2_ideology,
    h4_comparison_plot_p3_ideology, h4_comparison_plot_p4_ideology,
    ncol = 2, nrow = 2,
    top = "H4: Effect of Green Parties Moderated by Party Ideology"
  )
  ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_all_polynomial_comparison_ideology.png", h4_all_poly_comparison_ideology, width = 12, height = 10, dpi = 300)
}

# 4.5 Placebo Threshold Tests for H4 (Party Ideology) ----------------
h4_left_placebo <- run_placebo_threshold_test(
  data = clean_data_left_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  true_cutpoint = 0,
  placebo_range = c(-4, 4),
  placebo_step = 0.5,
  polynomial = 1,
  bandwidth = 2,
  covariates = c("country", "edate")
)

h4_right_placebo <- run_placebo_threshold_test(
  data = clean_data_right_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  true_cutpoint = 0,
  placebo_range = c(-4, 4),
  placebo_step = 0.5,
  polynomial = 1,
  bandwidth = 2,
  covariates = c("country", "edate")
)

# Plot placebo results
h4_left_placebo_plot <- plot_placebo_threshold_test(
  h4_left_placebo,
  title = "H4: Placebo Test (Left-wing Parties)"
)

h4_right_placebo_plot <- plot_placebo_threshold_test(
  h4_right_placebo,
  title = "H4: Placebo Test (Right-wing Parties)"
)

# Save placebo plots
ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_left_placebo.png", plot = h4_left_placebo_plot, width = 10, height = 6, dpi = 300)
ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_right_placebo.png", plot = h4_right_placebo_plot, width = 10, height = 6, dpi = 300)

# 4.6 Density Tests for H4 (Party Ideology) ----------------
# Add McCrary density test for left-wing parties
h4_left_density_test <- rddensity(clean_data_left_party$centered_lagged_pervote_samlet, c = 0, binoWStep = 0.250, binoW = 0.250)
h4_left_density_summary <- summary(h4_left_density_test)
h4_left_density_plot <- rdplotdensity(h4_left_density_test, 
                                    clean_data_left_party$centered_lagged_pervote_samlet,
                                    title = "H4: Density Test (Left-wing Parties)")

# Add McCrary density test for right-wing parties
h4_right_density_test <- rddensity(clean_data_right_party$centered_lagged_pervote_samlet, c = 0, binoWStep = 0.250, binoW = 0.250)
h4_right_density_summary <- summary(h4_right_density_test)
h4_right_density_plot <- rdplotdensity(h4_right_density_test, 
                                     clean_data_right_party$centered_lagged_pervote_samlet,
                                     title = "H4: Density Test (Right-wing Parties)")

summary(h4_left_density_test)
summary(h4_right_density_test)

# Save density plots
ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_left_density.png", plot = h4_left_density_plot$Estplot, width = 10, height = 6, dpi = 300)
ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_right_density.png", plot = h4_right_density_plot$Estplot, width = 10, height = 6, dpi = 300)

# 4.15 Outcome Placebo Tests for H4 (Party Ideology) ----------------
# Using variables that shouldn't be affected by treatment
placebo_vars <- c("rile_lowe", "per410") 

# Left-wing Parties
h4_left_outcome_placebo <- run_outcome_placebo_test(
  data = clean_data_left_party,
  real_outcome_var = "miljø_afhængig",
  placebo_outcome_vars = placebo_vars,
  running_var = "centered_lagged_pervote_samlet",
  polynomial = 1,
  bandwidth = 2,
  covariates = c("country", "edate")
)

h4_left_outcome_placebo_plot <- plot_outcome_placebo_test(
  h4_left_outcome_placebo,
  title = "H4: Outcome Placebo Test (Left-wing Parties)"
)

# Right-wing Parties
h4_right_outcome_placebo <- run_outcome_placebo_test(
  data = clean_data_right_party,
  real_outcome_var = "miljø_afhængig",
  placebo_outcome_vars = placebo_vars,
  running_var = "centered_lagged_pervote_samlet",
  polynomial = 1,
  bandwidth = 2,
  covariates = c("country", "edate")
)

h4_right_outcome_placebo_plot <- plot_outcome_placebo_test(
  h4_right_outcome_placebo,
  title = "H4: Outcome Placebo Test (Right-wing Parties)"
)

# Save outcome placebo plots
ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_left_outcome_placebo.png", plot = h4_left_outcome_placebo_plot, width = 8, height = 6, dpi = 300)
ggsave("Publisering Robusthedstests/H4 tests - Appendiks/Publisering h4_right_outcome_placebo.png", plot = h4_right_outcome_placebo_plot, width = 8, height = 6, dpi = 300)

# 4.7 Abou-Chadi & Krause (2020)-style robustness table for H4 ----------------
ck_style_table_h4_left <- build_ck_style_table(
  data = clean_data_left_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  treatment_var = "lagged_i_parlament",
  label = "H4 Left-Wing Parties",
  out_path_prefix = "Publisering Analyse/H4/Publisering h4_left_ck_style_table"
)

ck_style_table_h4_right <- build_ck_style_table(
  data = clean_data_right_party,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  treatment_var = "lagged_i_parlament",
  label = "H4 Right-Wing Parties",
  out_path_prefix = "Publisering Analyse/H4/Publisering h4_right_ck_style_table"
)

# ============================================================================
# 5. H5: PARTY SIZE EFFECT
# ============================================================================
# Opret først hovedmappen Robusthedstests, hvis den ikke allerede eksisterer
dir.create("Publisering Robusthedstests", showWarnings = FALSE)

# Opret derefter undermappen H4 tests - Appendiks
dir.create("Publisering Robusthedstests/H5 tests - Appendiks", showWarnings = FALSE)

# 2.2 Coefficient Stability Plots for H5 ----------------
h5_large_party_stability_plot  <- create_coefficient_stability_plot(
  data = large_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomials = c(1, 2, 3),
  covariates = c("country", "edate"),
  title = "H5: Effect on Large Parties"
)

h5_small_party_stability_plot  <- create_coefficient_stability_plot(
  data = small_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomials = c(1, 2, 3),
  covariates = c("country", "edate"),
  title = "H5: Effect on Small Parties"
)

ggsave("Publisering Robusthedstests/H5 tests - Appendiks/Publisering h5_large_party_stability_plot.png", plot = h5_large_party_stability_plot$plot, width = 10, height = 6, dpi = 300)

ggsave("Publisering Robusthedstests/H5 tests - Appendiks/Publisering h5_small_party_stability_plot.png", plot = h5_small_party_stability_plot$plot, width = 10, height = 6, dpi = 300)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h5_comparison_plot_p1_size <- compare_coefficient_stability(
  data_list = list(large_parties, small_parties),
  labels = c("Large Parties", "Small Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 1,
  covariates = c("country", "edate"),
  title = "H5: Effect of Green Parties (Polynomial Order 1)"
)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h5_comparison_plot_p2_size <- compare_coefficient_stability(
  data_list = list(large_parties, small_parties),
  labels = c("Large Parties", "Small Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 2,
  covariates = c("country", "edate"),
  title = "H5: Effect of Green Parties (Polynomial Order 2)"
)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h5_comparison_plot_p3_size <- compare_coefficient_stability(
  data_list = list(large_parties, small_parties),
  labels = c("Large Parties", "Small Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 3,
  covariates = c("country", "edate"),
  title = "H5: Effect of Green Parties (Polynomial Order 3)"
)

# 2.3 Comparison of Green Party Effects Across Polynomials ----------------
h5_comparison_plot_p4_size <- compare_coefficient_stability(
  data_list = list(large_parties, small_parties),
  labels = c("Large Parties", "Small Parties"),
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = seq(1, 3, by = 0.5),
  polynomial = 4,
  covariates = c("country", "edate"),
  title = "H5: Effect of Green Parties (Polynomial Order 4)"
)

if (requireNamespace("gridExtra", quietly = TRUE)) {
  h5_all_poly_comparison_size <- gridExtra::grid.arrange(
    h5_comparison_plot_p1_size, h5_comparison_plot_p2_size,
    h5_comparison_plot_p3_size, h5_comparison_plot_p4_size,
    ncol = 2, nrow = 2,
    top = "H5: Effect of Green Parties Moderated by Party Size"
  )
  ggsave("Publisering Robusthedstests/H5 tests - Appendiks/Publisering h5_all_polynomial_comparison_size.png", h5_all_poly_comparison_size, width = 12, height = 10, dpi = 300)
}

# 5.5 Placebo Threshold Tests for H5 (Party Size) ----------------
h5_large_placebo <- run_placebo_threshold_test(
  data = large_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  true_cutpoint = 0,
  placebo_range = c(-4, 4),
  placebo_step = 0.5,
  polynomial = 1,
  bandwidth = 2,
  covariates = c("country", "edate")
)

h5_small_placebo <- run_placebo_threshold_test(
  data = small_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  true_cutpoint = 0,
  placebo_range = c(-4, 4),
  placebo_step = 0.5,
  polynomial = 1,
  bandwidth = 2,
  covariates = c("country", "edate")
)

# Plot placebo results
h5_large_placebo_plot <- plot_placebo_threshold_test(
  h5_large_placebo,
  title = "H5: Placebo Test (Large Parties)"
)

h5_small_placebo_plot <- plot_placebo_threshold_test(
  h5_small_placebo,
  title = "H5: Placebo Test (Small Parties)"
)

# Save placebo plots
ggsave("Publisering Robusthedstests/H5 tests - Appendiks/Publisering h5_large_placebo_plot.png", plot = h5_large_placebo_plot, width = 10, height = 6, dpi = 300)
ggsave("Publisering Robusthedstests/H5 tests - Appendiks/Publisering h5_small_placebo_plot.png", plot = h5_small_placebo_plot, width = 10, height = 6, dpi = 300)

# 5.6 Density Tests for H4 (Party Size) ----------------
# Add McCrary density test for large parties
h5_large_density_test <- rddensity(large_parties$centered_lagged_pervote_samlet, c = 0, binoWStep = 0.250, binoW = 0.250)
h5_large_density_summary <- summary(h5_large_density_test)
h5_large_density_plot <- rdplotdensity(h5_large_density_test, 
                                    large_parties$centered_lagged_pervote_samlet,
                                    title = "H5: Density Test (Large Parties)")

# Add McCrary density test for right-wing parties
h5_small_density_test <- rddensity(small_parties$centered_lagged_pervote_samlet, c = 0, binoWStep = 0.250, binoW = 0.250)
h5_small_density_summary <- summary(h5_small_density_test)
h5_small_density_plot <- rdplotdensity(h5_small_density_test, 
                                     small_parties$centered_lagged_pervote_samlet,
                                     title = "H5: Density Test (Small Parties)")

summary(h5_large_density_test)
summary(h5_small_density_test)

# Save density plots
ggsave("Publisering Robusthedstests/H5 tests - Appendiks/Publisering h5_large_density.png", plot = h5_large_density_plot$Estplot, width = 10, height = 6, dpi = 300)
ggsave("Publisering Robusthedstests/H5 tests - Appendiks/Publisering h5_small_density.png", plot = h5_small_density_plot$Estplot, width = 10, height = 6, dpi = 300)

# 5.7 Abou-Chadi & Krause (2020)-style robustness table for H5 ----------------
ck_style_table_h5_large <- build_ck_style_table(
  data = large_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  treatment_var = "lagged_i_parlament",
  label = "H5 Large Parties",
  out_path_prefix = "Publisering Analyse/H5/Publisering h5_large_ck_style_table"
)

ck_style_table_h5_small <- build_ck_style_table(
  data = small_parties,
  outcome_var = "miljø_afhængig",
  running_var = "centered_lagged_pervote_samlet",
  treatment_var = "lagged_i_parlament",
  label = "H5 Small Parties",
  out_path_prefix = "Publisering Analyse/H5/Publisering h5_small_ck_style_table"
)

```

# ============================================================================
# 6. CULTURAL LIBERALISM OUTCOME (SECOND ISSUE DIMENSION)
# ============================================================================
# Green parties are not single-issue environmental parties -- they also mobilize on
# cultural liberalism, pro-immigration positions, and minority rights. This section
# re-estimates H1/H4/H5 with kultur_afhaengig (MARPOR per607/per608 multiculturalism
# log-ratio, see Data skabelse.Rmd) as the outcome instead of miljø_afhængig, so the
# environmental effect can be directly compared against a non-environmental Green
# party issue dimension. The running variable, cutoff, clustering, and sample
# construction are identical to H1/H4/H5 above; the manipulation/density test and
# sharp-vs-fuzzy check from section 1.3-1.4 apply unchanged since they depend only on
# the running variable, not the outcome, so they are not repeated here.

```{r cultural_analysis}
dir.create("Publisering Analyse/Cultural", showWarnings = FALSE)

# H1-equivalent: main effect on cultural liberalism -----------------------
h1_cultural_analysis_data <- final_dataset[complete.cases(final_dataset[, c("kultur_afhaengig",
                                                                 "centered_lagged_pervote_samlet",
                                                                 "lagged_i_parlament",
                                                                 "country",
                                                                 "edate",
                                                                 "country_election_id")]), ]

h1_rdd_cultural <- rdrobust(
  y = h1_cultural_analysis_data$kultur_afhaengig,
  x = h1_cultural_analysis_data$centered_lagged_pervote_samlet,
  c = 0,
  p = 1,
  kernel = "triangular",
  bwselect = "mserd",
  cluster = h1_cultural_analysis_data$country_election_id
)
check_rdrobust_cluster_count(h1_rdd_cultural, h1_cultural_analysis_data, "centered_lagged_pervote_samlet",
                              "country_election_id", "H1 cultural rdrobust")
summary(h1_rdd_cultural)

main_results_cultural <- data.frame(
  Outcome = "Cultural Liberalism Position",
  Bandwidth = round(h1_rdd_cultural$bws[1, 1], 3),
  LATE = round(h1_rdd_cultural$Estimate[1], 3),
  StdError = round(h1_rdd_cultural$se[1], 3),
  pvalue = round(h1_rdd_cultural$pv[1], 3),
  CI_Lower = round(h1_rdd_cultural$ci[1, 1], 3),
  CI_Upper = round(h1_rdd_cultural$ci[1, 2], 3)
)
main_results_cultural_table <- knitr::kable(main_results_cultural,
                                  caption = "Main RDD Results for H1 - Cultural Liberalism Outcome",
                                  col.names = c("Outcome Variable", "Bandwidth", "LATE", "Std. Error",
                                               "p-value", "95% CI Lower", "95% CI Upper"))
writeLines(main_results_cultural_table, file.path(getwd(), "Publisering Analyse/Cultural/Publisering h1_cultural_main_results.md"))
print(main_results_cultural_table)
write.csv(main_results_cultural, "Publisering Analyse/Cultural/Publisering h1_cultural_main_results.csv", row.names = FALSE)

# Robustness across bandwidths/polynomials, same specification as H1 section 3.1
results_df_h1_cultural <- run_rdd_robustness(
  data = h1_cultural_analysis_data,
  outcome_var = "kultur_afhaengig",
  running_var = "centered_lagged_pervote_samlet",
  bw_list = c(1, 1.5, 2, 2.5, 3, 3.5, 4),
  polynomials = c(1, 2, 3, 4),
  covariates = c("country", "edate"),
  group_label = "H1 Cultural"
)
selected_columns <- c("Group", "Polynomial", "Bandwidth", "LATE", "p_value", "StdErr", "N_left_of_c", "N_right_of_c")
write.csv(results_df_h1_cultural[, selected_columns], "Publisering Analyse/Cultural/Publisering h1_cultural_robustness_table.csv", row.names = FALSE)

# H4-equivalent: left/right moderation on cultural liberalism -------------
h4_cultural_analysis_data <- final_dataset[complete.cases(final_dataset[, c("kultur_afhaengig",
                                                                 "centered_lagged_pervote_samlet",
                                                                 "lagged_i_parlament",
                                                                 "left_party_lag1",
                                                                 "country",
                                                                 "edate",
                                                                 "country_election_id")]), ]
clean_data_right_party_cultural <- subset(h4_cultural_analysis_data, left_party_lag1 == 0)
clean_data_left_party_cultural <- subset(h4_cultural_analysis_data, left_party_lag1 == 1)

h4_rdd_right_cultural <- rdrobust(
    y = clean_data_right_party_cultural$kultur_afhaengig,
    x = clean_data_right_party_cultural$centered_lagged_pervote_samlet,
    c = 0, p = 1, kernel = "triangular", bwselect = "mserd",
    cluster = clean_data_right_party_cultural$country_election_id
  )
check_rdrobust_cluster_count(h4_rdd_right_cultural, clean_data_right_party_cultural, "centered_lagged_pervote_samlet",
                              "country_election_id", "H4 right-wing cultural rdrobust")
h4_rdd_left_cultural <- rdrobust(
    y = clean_data_left_party_cultural$kultur_afhaengig,
    x = clean_data_left_party_cultural$centered_lagged_pervote_samlet,
    c = 0, p = 1, kernel = "triangular", bwselect = "mserd",
    cluster = clean_data_left_party_cultural$country_election_id
  )
check_rdrobust_cluster_count(h4_rdd_left_cultural, clean_data_left_party_cultural, "centered_lagged_pervote_samlet",
                              "country_election_id", "H4 left-wing cultural rdrobust")

h4_cultural_results <- data.frame(
  Group = c("Right-Wing Parties", "Left-Wing Parties"),
  LATE = round(c(h4_rdd_right_cultural$Estimate[1], h4_rdd_left_cultural$Estimate[1]), 3),
  StdError = round(c(h4_rdd_right_cultural$se[1], h4_rdd_left_cultural$se[1]), 3),
  pvalue = round(c(h4_rdd_right_cultural$pv[1], h4_rdd_left_cultural$pv[1]), 3)
)
print(h4_cultural_results)
write.csv(h4_cultural_results, "Publisering Analyse/Cultural/Publisering h4_cultural_results.csv", row.names = FALSE)

# H5-equivalent: large/small party moderation on cultural liberalism ------
h5_cultural_analysis_data <- final_dataset[complete.cases(final_dataset[, c("kultur_afhaengig",
                                                                 "centered_lagged_pervote_samlet",
                                                                 "lagged_i_parlament",
                                                                 "large_party_lag1",
                                                                 "country",
                                                                 "edate",
                                                                 "country_election_id")]), ]
large_parties_cultural <- subset(h5_cultural_analysis_data, large_party_lag1 == 1)
small_parties_cultural <- subset(h5_cultural_analysis_data, large_party_lag1 == 0)

h5_rdd_large_cultural <- rdrobust(
    y = large_parties_cultural$kultur_afhaengig,
    x = large_parties_cultural$centered_lagged_pervote_samlet,
    c = 0, p = 1, kernel = "triangular", bwselect = "mserd",
    cluster = large_parties_cultural$country_election_id
  )
check_rdrobust_cluster_count(h5_rdd_large_cultural, large_parties_cultural, "centered_lagged_pervote_samlet",
                              "country_election_id", "H5 large-parties cultural rdrobust")
h5_rdd_small_cultural <- rdrobust(
    y = small_parties_cultural$kultur_afhaengig,
    x = small_parties_cultural$centered_lagged_pervote_samlet,
    c = 0, p = 1, kernel = "triangular", bwselect = "mserd",
    cluster = small_parties_cultural$country_election_id
  )
check_rdrobust_cluster_count(h5_rdd_small_cultural, small_parties_cultural, "centered_lagged_pervote_samlet",
                              "country_election_id", "H5 small-parties cultural rdrobust")

h5_cultural_results <- data.frame(
  Group = c("Large Parties", "Small Parties"),
  LATE = round(c(h5_rdd_large_cultural$Estimate[1], h5_rdd_small_cultural$Estimate[1]), 3),
  StdError = round(c(h5_rdd_large_cultural$se[1], h5_rdd_small_cultural$se[1]), 3),
  pvalue = round(c(h5_rdd_large_cultural$pv[1], h5_rdd_small_cultural$pv[1]), 3)
)
print(h5_cultural_results)
write.csv(h5_cultural_results, "Publisering Analyse/Cultural/Publisering h5_cultural_results.csv", row.names = FALSE)

# Side-by-side comparison: environmental vs. cultural-liberalism main effect ----
domain_comparison <- data.frame(
  Domain = c("Environmental (miljø_afhængig)", "Cultural Liberalism (kultur_afhaengig)"),
  LATE = round(c(h1_rdd$Estimate[1], h1_rdd_cultural$Estimate[1]), 3),
  StdError = round(c(h1_rdd$se[1], h1_rdd_cultural$se[1]), 3),
  pvalue = round(c(h1_rdd$pv[1], h1_rdd_cultural$pv[1]), 3),
  LATE_robust = round(c(h1_rdd$Estimate[3], h1_rdd_cultural$Estimate[3]), 3),
  StdError_robust = round(c(h1_rdd$se[3], h1_rdd_cultural$se[3]), 3),
  pvalue_robust = round(c(h1_rdd$pv[3], h1_rdd_cultural$pv[3]), 3),
  N = c(sum(h1_rdd$N_h), sum(h1_rdd_cultural$N_h))
)
domain_comparison_table <- knitr::kable(domain_comparison,
  caption = "Table: Green Party Parliamentary Entry Effect Across Issue Domains (Conventional and Robust bias-corrected, Calonico/Cattaneo/Titiunik 2014)")
writeLines(domain_comparison_table, file.path(getwd(), "Publisering Analyse/Cultural/Publisering domain_comparison.md"))
print(domain_comparison_table)
write.csv(domain_comparison, "Publisering Analyse/Cultural/Publisering domain_comparison.csv", row.names = FALSE)
```


####SKAL IKKE MED I DEN FÆRDIGE DATA TIL PUBLISERING --------------------
```{r Fuld Deskriptiv Statistik}
# Opret mappe til deskriptiv statistik hvis den ikke findes
dir.create("Publisering Deskriptiv Statistik", showWarnings = FALSE)

# 1. Basal deskriptiv statistik for nøglevariable ----------------

stats_tabel <- data.frame(
  Variabel = c(
    "Klimaposition (miljø_afhængig)",
    "Grønne partiers stemmeandel (centered_lagged_pervote_samlet)",
    "Grønne partier i parlament (lagged_i_parlament)",
    "Venstreorienteret parti (left_party_lag1)",
    "Stort parti (large_party_lag1)"
  ),
  Gennemsnit = c(
    mean(final_dataset$miljø_afhængig, na.rm = TRUE),
    mean(final_dataset$centered_lagged_pervote_samlet, na.rm = TRUE),
    mean(final_dataset$lagged_i_parlament, na.rm = TRUE),
    mean(final_dataset$left_party_lag1, na.rm = TRUE),
    mean(final_dataset$large_party_lag1, na.rm = TRUE)
  ),
  Median = c(
    median(final_dataset$miljø_afhængig, na.rm = TRUE),
    median(final_dataset$centered_lagged_pervote_samlet, na.rm = TRUE),
    median(final_dataset$lagged_i_parlament, na.rm = TRUE),
    median(final_dataset$left_party_lag1, na.rm = TRUE),
    median(final_dataset$large_party_lag1, na.rm = TRUE)
  ),
  Std_afvigelse = c(
    sd(final_dataset$miljø_afhængig, na.rm = TRUE),
    sd(final_dataset$centered_lagged_pervote_samlet, na.rm = TRUE),
    sd(final_dataset$lagged_i_parlament, na.rm = TRUE),
    sd(final_dataset$left_party_lag1, na.rm = TRUE),
    sd(final_dataset$large_party_lag1, na.rm = TRUE)
  ),
  Minimum = c(
    min(final_dataset$miljø_afhængig, na.rm = TRUE),
    min(final_dataset$centered_lagged_pervote_samlet, na.rm = TRUE),
    min(final_dataset$lagged_i_parlament, na.rm = TRUE),
    min(final_dataset$left_party_lag1, na.rm = TRUE),
    min(final_dataset$large_party_lag1, na.rm = TRUE)
  ),
  Maksimum = c(
    max(final_dataset$miljø_afhængig, na.rm = TRUE),
    max(final_dataset$centered_lagged_pervote_samlet, na.rm = TRUE),
    max(final_dataset$lagged_i_parlament, na.rm = TRUE),
    max(final_dataset$left_party_lag1, na.rm = TRUE),
    max(final_dataset$large_party_lag1, na.rm = TRUE)
  ),
  N = c(
    sum(!is.na(final_dataset$miljø_afhængig)),
    sum(!is.na(final_dataset$centered_lagged_pervote_samlet)),
    sum(!is.na(final_dataset$lagged_i_parlament)),
    sum(!is.na(final_dataset$left_party_lag1)),
    sum(!is.na(final_dataset$large_party_lag1))
  )
)

# Formatter tallene pænt
stats_tabel$Gennemsnit <- round(stats_tabel$Gennemsnit, 3)
stats_tabel$Median <- round(stats_tabel$Median, 3)
stats_tabel$Std_afvigelse <- round(stats_tabel$Std_afvigelse, 3)
stats_tabel$Minimum <- round(stats_tabel$Minimum, 3)
stats_tabel$Maksimum <- round(stats_tabel$Maksimum, 3)

tabel1 <- kable(stats_tabel, 
               caption = "Tabel A1: Deskriptiv statistik for nøglevariable i datasættet",
               format = "markdown")

# Gem som markdown-fil
writeLines(tabel1, "Publisering Deskriptiv Statistik/tabel1_deskriptiv_statistik.md")

# Gem også som CSV for backup
write.csv(stats_tabel, "Publisering Deskriptiv Statistik/tabel1_deskriptiv_statistik.csv", row.names = FALSE)

# 2. Lande i datasættet ----------------

land_stats <- final_dataset %>%
  group_by(countryname) %>%
  summarise(
    Antal_obs = n(),
    Første_år = min(edate, na.rm = TRUE),
    Sidste_år = max(edate, na.rm = TRUE),
    Antal_partier = n_distinct(party),
    Grønne_i_parlament = sum(lagged_i_parlament, na.rm = TRUE),
    Gns_klimaposition = round(mean(miljø_afhængig, na.rm = TRUE), 3)
  ) %>%
  arrange(desc(Antal_obs))

# Gem som markdown
tabel2 <- kable(land_stats, 
               caption = "Tabel A2: Oversigt over lande i datasættet",
               format = "markdown")

writeLines(tabel2, "Publisering Deskriptiv Statistik/tabel2_land_oversigt.md")
write.csv(land_stats, "Publisering Deskriptiv Statistik/tabel2_land_oversigt.csv", row.names = FALSE)

# 3. Partifamilier og klimaposition ----
if("parfam" %in% names(final_dataset)) {
  partifamilie_stats <- final_dataset %>%
    mutate(
      party_family = case_when(
      parfam == "10" ~ "Grønne",
      parfam == "20" ~ "Socialist/Andre venstreorienterede parties",
      parfam == "30" ~ "Social Demokratiske",
      parfam == "40" ~ "Liberale",
      parfam == "50" ~ "Kristendemokratiske",
      parfam == "60" ~ "Konservative",
      parfam == "70" ~ "Nationalistiske",
      parfam == "80" ~ "Agrarisk",
      parfam == "90" ~ "Etniske/Regionale",
      parfam == "95" ~ "Special emne partier",
      parfam == "98" ~ "Valgalliance uden leder",
      TRUE ~ "Andre"
      )
    ) %>%
    group_by(party_family) %>%
    summarise(
      Antal_obs = n(),
      Gns_klimaposition = round(mean(miljø_afhængig, na.rm = TRUE), 3),
      Median_klimaposition = round(median(miljø_afhængig, na.rm = TRUE), 3),
      Std_afv_klimaposition = round(sd(miljø_afhængig, na.rm = TRUE), 3)
    ) %>%
    arrange(desc(Gns_klimaposition))
  
  # Gem som markdown
  tabel3 <- kable(partifamilie_stats, 
                 caption = "Tabel A3: Klimapositioner efter partifamilie",
                 format = "markdown")
  
  writeLines(tabel3, "Publisering Deskriptiv Statistik/tabel3_partifamilie_stats.md")
  write.csv(partifamilie_stats, "Publisering Deskriptiv Statistik/tabel3_partifamilie_stats.csv", row.names = FALSE)
}

# 4. Missing data analyse -----
key_variables <- c("miljø_afhængig", "centered_lagged_pervote_samlet",
                  "lagged_i_parlament", "left_party_lag1",
                  "large_party_lag1", "good_economy_lag1", "GDP_per_capita_lag1",
                  "Unemployment", "Inflation-consumer prices")

# Sørg for at alle variable findes i datasættet
key_variables <- key_variables[key_variables %in% names(final_dataset)]

# Antal og procent af missing values
missing_stats <- data.frame(
  Variabel = key_variables,
  Antal_missing = sapply(final_dataset[, key_variables], function(x) sum(is.na(x))),
  Procent_missing = round(sapply(final_dataset[, key_variables], function(x) mean(is.na(x)) * 100), 1)
)

missing_stats <- missing_stats[order(-missing_stats$Procent_missing), ]

# Gem som markdown
tabel4 <- kable(missing_stats, 
               caption = "Tabel A4: Manglende værdier i nøglevariable",
               format = "markdown")

writeLines(tabel4, "Publisering Deskriptiv Statistik/tabel4_missing_data.md")
write.csv(missing_stats, "Publisering Deskriptiv Statistik/tabel4_missing_data.csv", row.names = FALSE)


# 5. Grønne partiers succes over tid --------
# Tjek først at de nødvendige variable findes. Year findes ikke som kolonne på
# final_dataset -- grupperer på edate ligesom stemmeandel_tid i sektion 8.
if(all(c("edate", "pervote_samlet", "i_parlament") %in% names(final_dataset))) {
  grønne_success_tid <- final_dataset %>%
    group_by(edate) %>%
    summarise(
      grønne_partier = sum(!is.na(pervote_samlet)),
      grønne_i_parlament = sum(i_parlament, na.rm = TRUE),
      success_rate = grønne_i_parlament / grønne_partier
    ) %>%
    filter(!is.na(success_rate))
  
  tabel5 <- kable(grønne_success_tid, 
                 caption = "Tabel A5: Grønne partiers succesrate over tid",
                 col.names = c("År", "Antal grønne partier", "Antal i parlament", "Succesrate"),
                 digits = 3,
                 format = "markdown")
  
  # Gem tabellen
  writeLines(tabel5, "Publisering Deskriptiv Statistik/tabel5_gronne_partiers_succes.md")
  write.csv(grønne_success_tid, "Publisering Deskriptiv Statistik/tabel5_gronne_partiers_succes.csv", row.names = FALSE)
}


# 6. Fordeling af klimaposition -------------
# Opret histogram over miljø_afhængig
p1 <- ggplot(final_dataset, aes(x = miljø_afhængig)) +
  geom_histogram(bins = 30, fill = "steelblue", color = "darkblue", alpha = 0.7) +
  geom_density(color = "red", size = 1) +
  labs(
    title = "Distribution of Environmental Focus (miljø_afhængig)",
    x = "Environmental Focus",
    y = "Amount"
  ) +
  theme_minimal()

# Gem plottet
ggsave("Publisering Deskriptiv Statistik/figur1_fordeling_klimaposition.png", p1, width = 10, height = 6, dpi = 300)


# 7. Klimaposition pr. land -----------
p2 <- ggplot(final_dataset, aes(x = reorder(countryname, miljø_afhængig, FUN = median, na.rm = TRUE), 
                              y = miljø_afhængig)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  coord_flip() +
  labs(
    title = "Environmental Focus per Country",
    x = "Country",
    y = "Environmental Focus"
  ) +
  theme_minimal()

# Gem plottet
ggsave("Publisering Deskriptiv Statistik/figur2_klimaposition_efter_land.png", p2, width = 10, height = 8, dpi = 300)


# 8. Grønne partiers stemmeandel over tid -----------
# Beregner gennemsnitlig stemmeandel for grønne partier pr. år
stemmeandel_tid <- final_dataset %>%
  group_by(edate) %>%
  summarise(
    gns_stemmeandel = mean(lagged_pervote_samlet, na.rm = TRUE),
    median_stemmeandel = median(lagged_pervote_samlet, na.rm = TRUE)
  ) %>%
  filter(!is.na(gns_stemmeandel))

p3 <- ggplot(stemmeandel_tid, aes(x = edate)) +
  geom_line(aes(y = gns_stemmeandel), size = 1, color = "darkgreen") +
  geom_line(aes(y = median_stemmeandel), size = 1, color = "green", linetype = "dashed") +
  labs(
    title = "Grønne partiers stemmeandel over tid",
    x = "År",
    y = "Stemmeandel (%)",
    caption = "Kilde: Egne beregninger baseret på Manifesto Project Dataset"
  ) +
  theme_minimal()

# Gem plottet
ggsave("Publisering Deskriptiv Statistik/figur3_stemmeandel_over_tid.png", p3, width = 10, height = 6, dpi = 300)

# 9. Threshold oversigt -----
# Lav en ren tabel med thresholds uden party-kolonnen
threshold_oversigt <- final_dataset %>%
  # Gruppér efter land og valgdato for at fjerne dubletter på grund af partier
  group_by(countryname, edate) %>%
  # Tag kun én threshold-værdi per land/valgdato (da alle bør være identiske)
  summarise(threshold = first(threshold), .groups = "drop") %>%
  # Fjern rækker med manglende threshold-værdier
  filter(!is.na(threshold)) %>%
  # Sortér efter land og valgdato
  arrange(countryname, edate)

# Se de første rækker for at bekræfte at tabellen er korrekt
print(head(threshold_oversigt))

# Gem som CSV-fil
write.csv(threshold_oversigt, "Publisering Deskriptiv Statistik/threshold_by_country_year.csv", row.names = FALSE)

# Lav en pæn tabel med knitr
tabel6 <- kable(threshold_oversigt, 
               caption = "Tabel A6: Valggrænser (thresholds) efter land og år",
               col.names = c("Land", "Valgdato", "Valggrænse (%)"),
               format = "markdown")

# Gem som markdown-fil
writeLines(tabel6, "Publisering Deskriptiv Statistik/tabel6_threshold_by_country_year.md")


# 10. Deskriptiv statistik for hver hypotese -----

# H1: Grønne partier i parlament
# Forventer at du har et datasæt kaldet h1_analysis_data
if(exists("h1_analysis_data")) {
  h1_stats <- h1_analysis_data %>%
    group_by(lagged_i_parlament) %>%
    summarise(
      Antal_obs = n(),
      Gns_klimaposition = round(mean(miljø_afhængig, na.rm = TRUE), 3),
      Median_klimaposition = round(median(miljø_afhængig, na.rm = TRUE), 3),
      Std_afv_klimaposition = round(sd(miljø_afhængig, na.rm = TRUE), 3),
      Min_klimaposition = round(min(miljø_afhængig, na.rm = TRUE), 3),
      Max_klimaposition = round(max(miljø_afhængig, na.rm = TRUE), 3)
    ) %>%
    mutate(
      Gruppe = case_when(
        lagged_i_parlament == 0 ~ "Ingen grønne partier i parlament",
        lagged_i_parlament == 1 ~ "Grønne partier i parlament",
        TRUE ~ "Ukendt"
      )
    ) %>%
    select(Gruppe, Antal_obs, Gns_klimaposition, Median_klimaposition, 
           Std_afv_klimaposition, Min_klimaposition, Max_klimaposition)
  
  tabel7 <- kable(h1_stats,
                 caption = "Tabel A7: Deskriptiv statistik for H1 - Grønne partier i parlament",
                 format = "markdown")
  writeLines(tabel7, "Publisering Deskriptiv Statistik/tabel7_h1_stats.md")
  

  
}

# H4: Venstreorienterede partier
if(exists("h4_analysis_data")) {
  h4_stats <- h4_analysis_data %>%
    group_by(left_party_lag1, lagged_i_parlament) %>%
    summarise(
      Antal_obs = n(),
      Gns_klimaposition = round(mean(miljø_afhængig, na.rm = TRUE), 3),
      Median_klimaposition = round(median(miljø_afhængig, na.rm = TRUE), 3),
      Std_afv_klimaposition = round(sd(miljø_afhængig, na.rm = TRUE), 3)
    ) %>%
    mutate(
      Gruppe = case_when(
        left_party_lag1 == 0 & lagged_i_parlament == 0 ~ "Højreorienteret parti, ingen grønne i parlament",
        left_party_lag1 == 0 & lagged_i_parlament == 1 ~ "Højreorienteret parti, grønne i parlament",
        left_party_lag1 == 1 & lagged_i_parlament == 0 ~ "Venstreorienteret parti, ingen grønne i parlament",
        left_party_lag1 == 1 & lagged_i_parlament == 1 ~ "Venstreorienteret parti, grønne i parlament",
        TRUE ~ "Ukendt"
      )
    ) %>%
    select(Gruppe, Antal_obs, Gns_klimaposition, Median_klimaposition, Std_afv_klimaposition)
  
  tabel10 <- kable(h4_stats,
                  caption = "Tabel A10: Deskriptiv statistik for H4 - Venstreorienterede partier",
                  format = "markdown")
  writeLines(tabel10, "Publisering Deskriptiv Statistik/tabel10_h4_stats.md")
  

 
}

# H5: Store partier
if(exists("h5_analysis_data")) {
  h5_stats <- h5_analysis_data %>%
    group_by(large_party_lag1, lagged_i_parlament) %>%
    summarise(
      Antal_obs = n(),
      Gns_klimaposition = round(mean(miljø_afhængig, na.rm = TRUE), 3),
      Median_klimaposition = round(median(miljø_afhængig, na.rm = TRUE), 3),
      Std_afv_klimaposition = round(sd(miljø_afhængig, na.rm = TRUE), 3)
    ) %>%
    mutate(
      Gruppe = case_when(
        large_party_lag1 == 0 & lagged_i_parlament == 0 ~ "Lille parti, ingen grønne i parlament",
        large_party_lag1 == 0 & lagged_i_parlament == 1 ~ "Lille parti, grønne i parlament",
        large_party_lag1 == 1 & lagged_i_parlament == 0 ~ "Stort parti, ingen grønne i parlament",
        large_party_lag1 == 1 & lagged_i_parlament == 1 ~ "Stort parti, grønne i parlament",
        TRUE ~ "Ukendt"
      )
    ) %>%
    select(Gruppe, Antal_obs, Gns_klimaposition, Median_klimaposition, Std_afv_klimaposition)
  
  tabel11 <- kable(h5_stats,
                  caption = "Tabel A11: Deskriptiv statistik for H5 - Store partier",
                  format = "markdown")
  writeLines(tabel11, "Publisering Deskriptiv Statistik/tabel11_h5_stats.md")

}

# 10b. Case distribution: small vs. large mainstream parties, and over time ------
# Addresses reviewer question on case distribution: how many small vs. large
# mainstream parties are in the data, and how Green party parliamentary entry is
# distributed over the sample's time span (1970s-2020s).
if("large_party_lag1" %in% names(final_dataset)) {
  case_distribution_size <- final_dataset %>%
    filter(!is.na(large_party_lag1)) %>%
    mutate(Størrelse = ifelse(large_party_lag1 == 1, "Stort mainstreamparti", "Lille mainstreamparti")) %>%
    group_by(Størrelse) %>%
    summarise(
      Antal_partiobservationer = n(),
      Antal_unikke_partier = n_distinct(party),
      .groups = "drop"
    )

  tabel12 <- kable(case_distribution_size,
                 caption = "Tabel A12: Antal store vs. små mainstreampartier i datasættet",
                 format = "markdown")
  writeLines(tabel12, "Publisering Deskriptiv Statistik/tabel12_case_distribution_size.md")
  write.csv(case_distribution_size, "Publisering Deskriptiv Statistik/tabel12_case_distribution_size.csv", row.names = FALSE)
}

if(all(c("edate", "i_parlament") %in% names(final_dataset))) {
  # Year isn't a column on final_dataset -- derive it from edate. edate may already
  # be a Date (from manifestoR) or a character string in "YYYY/MM/DD" format (from
  # the green party merge), so parse defensively rather than assuming either.
  case_distribution_decade <- final_dataset %>%
    mutate(
      Election_Year = if (inherits(edate, "Date")) {
        lubridate::year(edate)
      } else {
        lubridate::year(lubridate::ymd(as.character(edate)))
      }
    ) %>%
    filter(!is.na(Election_Year)) %>%
    mutate(Decade = floor(Election_Year / 10) * 10) %>%
    group_by(Decade) %>%
    summarise(
      Antal_observationer = n(),
      Antal_lande = n_distinct(countryname),
      Grønne_i_parlament_andel = round(mean(i_parlament, na.rm = TRUE), 3),
      .groups = "drop"
    )

  tabel13 <- kable(case_distribution_decade,
                 caption = "Tabel A13: Antal observationer og grønne partiers parlaments-andel efter årti",
                 col.names = c("Årti", "Antal observationer", "Antal lande", "Andel grønne i parlament"),
                 format = "markdown")
  writeLines(tabel13, "Publisering Deskriptiv Statistik/tabel13_case_distribution_decade.md")
  write.csv(case_distribution_decade, "Publisering Deskriptiv Statistik/tabel13_case_distribution_decade.csv", row.names = FALSE)
}

# Note on formation-to-parliament-entry lag (reviewer question): this cannot be
# computed from the current data. MARPOR/ParlGov coverage begins in the early
# 1970s for most countries, so for any Green party first observed at the start of
# the sample we cannot tell whether that observation is close to the party's actual
# founding or the party already existed for years beforehand (left-censoring) -- no
# founding-date variable exists in either MARPOR or ParlGov for this purpose. This
# is documented here rather than computed with placeholder/incomplete dates.
cat("\nNote: Green party formation-to-parliament-entry lag is not computed --",
    "MARPOR/ParlGov data start ~1972, so founding dates before the sample window",
    "are left-censored and unknown for parties already active at that point.\n")


# 11. Samlet tabel -----
# Lav en samlet dokument med alle tabeller
tabeller_samlet <- c(
  "# Deskriptiv statistik\n\n",
  "## Tabel A1: Deskriptiv statistik for nøglevariable\n\n",
  tabel1,
  "\n\n## Tabel A2: Oversigt over lande i datasættet\n\n",
  tabel2
)

if(exists("tabel3")) {
  tabeller_samlet <- c(tabeller_samlet, 
                     "\n\n## Tabel A3: Klimapositioner efter partifamilie\n\n",
                     tabel3)
}

tabeller_samlet <- c(tabeller_samlet,
                   "\n\n## Tabel A4: Manglende værdier i nøglevariable\n\n",
                   tabel4)

if(exists("tabel5")) {
  tabeller_samlet <- c(tabeller_samlet, 
                     "\n\n## Tabel A5: Grønne partiers succesrate over tid\n\n",
                     tabel5)
}

tabeller_samlet <- c(tabeller_samlet,
                   "\n\n## Tabel A6: Valggrænser (thresholds) efter land og år\n\n",
                   tabel6)

# Tilføj de nye tabeller hvis de eksisterer
if(exists("tabel7")) {
  tabeller_samlet <- c(tabeller_samlet,
                     "\n\n## Tabel A7: Deskriptiv statistik for H1 - Grønne partier i parlament\n\n",
                     tabel7)
}

if(exists("tabel9")) {
  tabeller_samlet <- c(tabeller_samlet,
                     "\n\n## Tabel A9: Deskriptiv statistik for H3 - Økonomiske forhold\n\n",
                     tabel9)
}

if(exists("tabel9b")) {
  tabeller_samlet <- c(tabeller_samlet,
                     "\n\n## Tabel A9b: Deskriptiv statistik for H3 - BNP-vækst\n\n",
                     tabel9b)
}

if(exists("tabel10")) {
  tabeller_samlet <- c(tabeller_samlet,
                     "\n\n## Tabel A10: Deskriptiv statistik for H4 - Venstreorienterede partier\n\n",
                     tabel10)
}

if(exists("tabel11")) {
  tabeller_samlet <- c(tabeller_samlet,
                     "\n\n## Tabel A11: Deskriptiv statistik for H5 - Store partier\n\n",
                     tabel11)
}

if(exists("tabel12")) {
  tabeller_samlet <- c(tabeller_samlet,
                     "\n\n## Tabel A12: Antal store vs. små mainstreampartier\n\n",
                     tabel12)
}

if(exists("tabel13")) {
  tabeller_samlet <- c(tabeller_samlet,
                     "\n\n## Tabel A13: Case-fordeling efter årti\n\n",
                     tabel13)
}

# Gem den opdaterede samlede dokument
writeLines(tabeller_samlet, "Publisering Deskriptiv Statistik/alle_tabeller.md")

# Bekræft at filerne er blevet gemt
liste_filer <- list.files("Deskriptiv Statistik", full.names = TRUE)
print(liste_filer)

# Afsluttende besked
cat("\nDeskriptiv statistik er nu gemt i mappen 'Deskriptiv Statistik'.\n")
cat("Der er genereret både markdown (.md) og csv-filer samt visualiseringer (.png).\n")
```

